---
title: "ESCAN"
author: "Helio"
date: "02/06/2021"
output: html_document
---
What to sue fo the presentation
- is alexithymia related to concordance - pupil and arousal better concordance -
- pupil atenuated relation for alexithymic 9 both aggregated plot, and the the lmer plot

- SCR relicateded LMMS
- additional low SCR effect

```{r}
library(gghalves)

# pupil tracks arousal

db_full4new_stim_screen_pupil_nopract %>%
    subset(pp_arousal_outler== FALSE)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
    group_by(ssid, ground_arousal_lab, Alexithymia)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_arousal_lab, pup_basCor, color = ground_arousal_lab,fill = ground_arousal_lab))+
      
  
 geom_half_violin(colour = FALSE, alpha = .3, size = 5)+
     # geom_bar(stat="summary", fun.y = "mean", width = .2)+
      geom_jitter(width = .1, alpha=.2)+
    stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  stat_summary(geom = 'pointrange', width =1)+
  p$graphstyle+
  xlab("Arousal")+
  ylab("Baseline corrected pupil")+
  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")


install.packages("ggside")
library(ggExtra)
library(ggside)

pupil_arousal<- db_full4new_stim_screen_pupil_nopract %>%
    subset(pp_arousal_outler== FALSE)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
    group_by(ssid, ground_arousal_lab, Alexithymia)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_arousal_lab, pup_basCor,fill = ground_arousal_lab))+
 # geom_half_violin(colour = FALSE, alpha = .3, size = 5)+
     geom_bar(stat="summary", fun.y = "mean", alpha = .3, width = .5)+
      geom_jitter(aes(color = ground_arousal_lab),width = .1, alpha=.2)+
    stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = .4, colour = "Black") +
  stat_summary(geom = 'pointrange', width =1)+
    geom_ysidedensity(aes(x=stat(density),color = ground_arousal_lab), alpha = .4)+
  # geom_xsidedensity(aes(y=stat(density)), color = FALSE, alpha = .5)+
  p$graphstyle+
  xlab("Arousal")+
  ylab("Baseline corrected pupil")+
  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")

pupil_arousal

ggsave("pupil_arousal.png", pupil_arousal, device = "png", width = 10, height = 7, dpi = 800)
  



```


Pupil tracks valence

```{r}

db_full4new_stim_screen_pupil_nopract %>%
    subset(pp_arousal_outler== FALSE)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
    group_by(ssid, ground_valence_lab, Alexithymia)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_valence_lab, pup_basCor,fill = ground_valence_lab))+
 # geom_half_violin(colour = FALSE, alpha = .3, size = 5)+
     geom_bar(stat="summary", fun.y = "mean", alpha = .3, width = .5)+
      geom_jitter(aes(color = ground_valence_lab),width = .1, alpha=.2)+
    stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = .4, colour = "Black") +
  stat_summary(geom = 'pointrange', width =1)+
    geom_ysidedensity(aes(x=stat(density),color = ground_valence_lab), alpha = .4)+
  # geom_xsidedensity(aes(y=stat(density)), color = FALSE, alpha = .5)+
  p$graphstyle+
  xlab("Arousal")+
  ylab("Baseline corrected pupil")+
  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")


```

Pupil tracks alexithymia effeccts
```{r}
ground_valence_lab

library(ggside)
library(ggExtra)
db_full4new_stim_screen_pupil_nopract %>%
  # subset(Group == "NT")%>%
   subset(pp_arousal_outler== FALSE)%>%
  subset(pupil_outlier == FALSE)%>%
  # subset(!is.na(Alexithymia))%>%
  # subset(pupil_outlier == FALSE & arousal_outler == FALSE & !is.na(Alexithymia) & ssid != 610)%>%
  group_by(ssid, Alexithymia)%>%
  mutate(cor_arousal_self_pup = cor.test(arousal, pup_basCor, use = 'complete.obs')$estimate)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(TASc,psych::fisherz2r(cor_arousal_self_pup)))+
  geom_point(size =2)+
  geom_ysidedensity(aes(x=stat(density), alpha = .4))+
   geom_xsidedensity(aes(y=stat(density), alpha = .4))+
  # geom_xsidedensity(aes(x=stat(density), alpha = .4))+
  # geom_xsidedensity(aes(x=stat(density),color = ground_arousal_lab), alpha = .4)+
  # geom_smooth(method = 'lm', se = F)+
  geom_smooth(method=lm, se=FALSE, linetype="dashed",
             color="darkred")+
  ggpubr::stat_cor()+
  xlab("Alexithymia (Z)")+
  ylab("Subjective/Objective arousal matching")+
p$graphstyle
  


```




```{r}
interactions::interact_plot(pupil_models$pupil_tas_to_arousal, pred = pup_basCor, modx = TASc)+
  xlab("Baseline corrected pupil")+
  ylab("Self reported arousal")+
  theme_bw()
  p$graphstyle


```


SCR
```{r}
db_full4new_stim_screen_pupil_nopract <- db_full4new_stim_screen_pupil_nopract %>%
    # subset(pp_arousal_outler == FALSE)%>%
  # subset(arousal_outler == FALSE)%>%
  # subset(pupil_outlier == FALSE & arousal_outler == FALSE & !is.na(Alexithymia))%>%
   group_by(ssid)%>%
  mutate(BIO_CDA.PhasicMax_z = scale(BIO_CDA.PhasicMax, center = TRUE)[,1])%>%
  mutate(BIO_CDA.AmpSum_z = scale(BIO_CDA.AmpSum, center = TRUE)[,1])%>%
  mutate(BIO_CDA.ISCR_z = scale(BIO_CDA.ISCR, center = TRUE)[,1])%>%
  mutate(BIO_CDA.SCR_z = scale(BIO_CDA.SCR, center = TRUE)[,1])%>%
  ungroup()%>%
  mutate(BIO_CDA.PhasicMax_z_acrossall = scale(BIO_CDA.PhasicMax, center = TRUE)[,1])
  



scr_models$escan1<- lmer(BIO_CDA.SCR_z ~ arousal_c+ (1|ssid) + (1|stimIAPS),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract, !is.na(Alexithymia)))

summary(scr_models$escan1)

# the 
scr_models$escan<- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ TASc*arousal_c * valence_c+(1|ssid) + (1|stimIAPS),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract, Group == "NT" &!is.na(Alexithymia)))


scr_models$escan<- lmer(arousal_c ~ TASc*BIO_CDA.PhasicMax_z  + (1|ssid) + (1|stimIAPS),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract, !is.na(Alexithymia)))


summary(scr_models$escan)

db_full4new_stim_screen_pupil_nopract %>%
  # subset(Group == "NT")%>%
   # subset(pp_arousal_outler== FALSE)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  mutate(logBIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
  group_by(ssid,Alexithymia)%>%
  mutate(logBIO_CDA.PhasicMax_mean = mean(logBIO_CDA.PhasicMax, na.rm = TRUE))%>%
  group_by(ssid,stimIAPS)%>%
  mutate(logBIO_CDA.PhasicMax_mean_stim = mean(logBIO_CDA.PhasicMax, na.rm = TRUE))%>%
  # summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(TASc,logBIO_CDA.PhasicMax))+
  # stat_summary(geom = 'pointrange')+
  
  geom_smooth(aes(group = stimIAPS, y =logBIO_CDA.PhasicMax_mean_stim), method=lm, se=FALSE, colour = "gray40", alpha = .01,linetype="dashed", size = .2 )+
  geom_smooth( method=lm, se=FALSE, linetype="dashed",
             color="darkred", size = 2)+
  stat_summary(geom = 'pointrange', pch = 1)+
   # geom_ysidedensity(aes(x=stat(density), alpha = .4))+
   # geom_xsidedensity(aes(y=stat(density), alpha = .4))+
    # geom_point(aes(color = ssid),size =2, pch  = 1)+
  
  
  # ggpubr::stat_cor()+
  xlab("Alexithymia (Z)")+
  ylab("SCR")+
p$graphstyle


```




```{r}
db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler == FALSE)%>%
  subset( arousal_outler == FALSE )%>%
       subset(!is.na(Alexithymia))%>%
  ungroup()%>%
   # group_by(ssid)%>%
  mutate(BIO_CDA.PhasicMax_z = scale(BIO_CDA.PhasicMax, center = TRUE)[,1])%>%
  ungroup()%>%
    group_by(ssid, Alexithymia)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(Alexithymia, y = BIO_CDA.PhasicMax_z, fill = Alexithymia))+

  stat_summary(geom = 'pointrange')+
  geom_bar(stat="summary", fun.y = "mean", alpha = .2, width = .5)+
   # geom_boxplot(alpha = .1)+
  geom_jitter(width = .15, alpha = .2)+
   geom_ysidedensity(aes(x=stat(density)), alpha = .4)+
  ylim(-.7,2)+
    xlab("Alexithymia (Z)")+
  ylab("SCR")+
  p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")
  



summary(lmer(BIO_CDA.PhasicMax ~  TASc *arousal_c*valence_c+ (1|ssid) + (1|stimIAPS),
     REML = FALSE,
     data = db_full4new_stim_screen_pupil_nopract))


```




```{r}


mutate(logBIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
  group_by(ssid,Alexithymia)%>%
  mutate(logBIO_CDA.PhasicMax_mean = mean(logBIO_CDA.PhasicMax, na.rm = TRUE))%>%
  group_by(ssid,stimIAPS)
  
  library
db_full4new_stim_screen_pupil_nopract %>%
    # subset(pp_arousal_outler== FALSE)%>%
  # subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
    group_by(ssid, mediansplit_sample_arousal2, Alexithymia, mediansplit_sample_valence2)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_sample_arousal2, BIO_CDA.PhasicMax_z,fill = mediansplit_sample_arousal2))+
 # geom_half_violin(colour = FALSE, alpha = .3, size = 5)+
     geom_bar(stat="summary", fun.y = "mean", alpha = .3, width = .5)+
  # geom_boxplot()+
      geom_jitter(aes(color = mediansplit_sample_arousal2),width = .1, alpha=.2)+
    stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = .4, colour = "Black") +
  stat_summary(geom = 'pointrange', width =1)+
    # geom_ysidedensity(aes(x=stat(density),color = ground_arousal_lab), alpha = .4)+
  # geom_xsidedensity(aes(y=stat(density)), color = FALSE, alpha = .5)+
  p$graphstyle+
  xlab("Arousal")+
  ylab("SCR (z)")+
  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  geom_hline(yintercept = 0, linetype = "dashed")+
  facet_grid(~mediansplit_sample_valence2)+
  ggpubr::stat_compare_means()




db_full4new_stim_screen_pupil_nopract %>%
    # subset(pp_arousal_outler== FALSE)%>%
  # subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
    group_by(ssid, Alexithymia, mediansplit_sample_valence2)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  mutate(BIO_CDA.PhasicMax_z_f_diff = BIO_CDA.PhasicMax_z[mediansplit_sample_valence2 == "More positive"]-
           BIO_CDA.PhasicMax_z[mediansplit_sample_valence2 == "More negative"])%>%
  subset(BIO_CDA.PhasicMax_z_f_diff<0)%>%
  ggplot(aes(mediansplit_sample_valence2, BIO_CDA.PhasicMax_z,fill = mediansplit_sample_valence2))+
 # geom_half_violin(colour = FALSE, alpha = .3, size = 5)+
     geom_bar(stat="summary", fun.y = "mean", alpha = .3, width = .5)+
  # geom_boxplot()+
      geom_jitter(aes(color = mediansplit_sample_valence2),width = .1, alpha=.2)+
    stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = .4, colour = "Black") +
  stat_summary(geom = 'pointrange', width =1)+
    # geom_ysidedensity(aes(x=stat(density),color = ground_arousal_lab), alpha = .4)+
  # geom_xsidedensity(aes(y=stat(density)), color = FALSE, alpha = .5)+
  p$graphstyle+
  xlab("Arousal")+
  ylab("SCR (z)")+
  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  geom_hline(yintercept = 0, linetype = "dashed")+
  # facet_grid(~mediansplit_sample_valence2)+
  ggpubr::stat_compare_means()



db_full4new_stim_screen_pupil_nopract_nt %>%
  subset(!is.na(mediansplit_sample_valence2))%>%
  subset(!is.na(BIO_CDA.PhasicMax_z))%>%
    # subset(pp_arousal_outler== FALSE)%>%
  # subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
    group_by(ssid, Alexithymia, mediansplit_sample_valence2)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  mutate(BIO_CDA.PhasicMax_z_f_diff = BIO_CDA.PhasicMax_z[mediansplit_sample_valence2 == "More positive"]-
           BIO_CDA.PhasicMax_z[mediansplit_sample_valence2 == "More negative"])%>%
  # subset(BIO_CDA.PhasicMax_z_f_diff<0)%>%
  mutate(bowtie = if_else(BIO_CDA.PhasicMax_z_f_diff>0, "pos", "neg"))%>%
  # group_by(ssid, bowtie)%>%
    # summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  
  ggplot(aes(AQ,BIO_CDA.PhasicMax_z))+
  geom_point()+
  geom_smooth(method = 'lm',se = F)+
  facet_grid(~bowtie)


  geom_point()
  geom_jitter(alpha = .1, width =.1)+
  stat_summary(geom = 'pointrange', width =1)
  # geom_smooth(method = 'lm')
 # geom_half_violin(colour = FALSE, alpha = .3, size = 5)+
     # geom_bar(stat="summary", fun.y = "mean", alpha = .3, width = .5)

```

  # geom_boxplot()+
      geom_jitter(aes(color = mediansplit_sample_valence2),width = .1, alpha=.2)+
    stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = .4, colour = "Black") +
  stat_summary(geom = 'pointrange', width =1)+
    # geom_ysidedensity(aes(x=stat(density),color = ground_arousal_lab), alpha = .4)+
  # geom_xsidedensity(aes(y=stat(density)), color = FALSE, alpha = .5)+
  p$graphstyle+
  xlab("Arousal")+
  ylab("SCR (z)")+
  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  geom_hline(yintercept = 0, linetype = "dashed")+
  # facet_grid(~mediansplit_sample_valence2)+
  ggpubr::stat_compare_means()


```
