---
title: "preprocess_hdf5_2023"
author: "Helio"
date: "2023-02-01"
output: html_document
---

# Overview 
In this file I aim to process all the gaze data, essentially read, clean and combines multiple files with gaze data and their metadata

# Conventions
For data: dta_
Temporary files: tmp_
Statistical summaries: sum_
Models (such as lm models): mod_
Custom functions: fn_
Plots and visualization: plt_
Lookup and referecne tables: lkp_
Results and Analysis: rlt_
Consistency and accuracy checks: chk_

Set-up: where I load libraries and create objects for later use (such as color schemes etc).

SETUP

```{r}
# if (!requireNamespace("BiocManager", quietly = TRUE))
#     install.packages("BiocManager")
# BiocManager::install(version = "3.10")
# 
# BiocManager::install("rhdf5")

library(rhdf5)

library(tidyverse)
library(purrr)
library(data.table)
library(dplyr)
library(tidyr)
# library(gazer)

```

data import and cleaning

```{r, gp extractor}

hdf5FilesPath<- "~/Library/CloudStorage/GoogleDrive-helioclemente.c@gmail.com/My Drive/Papers 2022/InteroceptionStudy/InteroStudy2020/Data Collection 2019- 2020/2022/iaps/EYETRACKER" # edit to your data path


gp.extractor = function(hdf5FilesPath) {
  
  setwd(hdf5FilesPath) #sets a path
  
  # return a list of hdf5 files in the path
  hdfFilesList = list.files(hdf5FilesPath, pattern = "\\.hdf5$")
  
  if (length(hdfFilesList) == 0){
    
    return(message('No HDF5 files found in the directory provided.'))
  }
   # loop over the list and load each file to data
  # f = 2
  for (f in 1:length(hdfFilesList)) {
    
    message(sprintf("Extracting file %i / %i - %s", f, length(hdfFilesList), hdfFilesList[f]))
    
    
    # the line below loads eyatracking and meatadata into different temporary datasets
    #note that some r-studio bug sometimes causes this to fail when running from notebook, 
    # in that case run it directly on command line
    tmp.events =h5read(hdfFilesList[f], '/data_collection/events/experiment/MessageEvent') # metadata = what stimuli, start and end times, etc
    
    # check what we should expect in terms of numbers
  # 56 trials + 1 rest period
    # 57 (fixation, stim, valence, intensity)
    # 57*(4*2)
    # nrow(tmp.events)-456
    
    # unique(substr(tmp.events$text,1,6))
    
    # store the eyetracking data
    tmp.eyetr  = h5read(hdfFilesList[f], '/data_collection/events/eyetracker/BinocularEyeSampleEvent') #contains eyetarckign data, gaze coordinates, etc
    
    # Get subject id from Events
    ssid = sapply(strsplit(grep('SubjJID', tmp.events$text, value = TRUE), split = ": "), "[", 2)
    date = sapply(strsplit(grep('DATE', tmp.events$text, value = TRUE), split = ": "), "[", 2)
    session = sapply(strsplit(grep('Session:', tmp.events$text, value = TRUE), split = ":"), "[", 2)
    cali<- subset(tmp.events, grepl('Cali', tmp.events$text) == TRUE)
    
    # Create DF for trials data
    tmp.df = data.frame(matrix(ncol = ncol(tmp.eyetr)))
    names(tmp.df) = names(tmp.eyetr) #
    # colnames(tmp.df)
    
    # Prepare Events, keep only start/end messages
    phrases = c('tStart', 'tEnd')
    
    # tmp.events_backup<- tmp.events
    # tmp.events<-  tmp.events_backup
    
    tmp.events = subset(tmp.events, grepl(paste(phrases, collapse = "|"), tmp.events$text))
    # currently 450
    
    # Create start/end references
    tmp.events$tStart   = NA
    tmp.events$tEnd     = NA
    
    # Trial number extraction 
    tmp.events$tNo      = NA
    tmp.df$tNo          = NA
    tmp.df$Condition    = NA
    
    # Space for subject id
    tmp.df$ssid         = NA
    tmp.df$text<-NA
    
    # store times for start and end of triggers
    for (l in 1:nrow(tmp.events)) {
 
      message(sprintf("Grabing start messages %s", tmp.events$text[l]))
      
      if ((grepl('tStart', tmp.events$text[l])) == TRUE) {
        tmp.events$tStart[l] = tmp.events$time[l]
        
        if ((grepl('tEnd', tmp.events$text[l+1])) == TRUE){
          tmp.events$tEnd[l] = tmp.events$time[l+1]
        }
        
        else {
          message('trial start/end structure not valid')
        }
      }
      
    }
    
    message(sprintf("done grabbing messages"))
    # readline(prompt="Press [enter] to continue")
    
    tmp.events$tNo<- as.numeric(as.character(gsub(".*_","",tmp.events$text)))

     message(sprintf("making screencontent"))
     
     tmp.eventsbackup<- tmp.events
    
     tmp.events$screencontent<- if_else(grepl('fixation', tmp.events$text), 'fixation',
                                       if_else(grepl('Valence', tmp.events$text), 'ValenceResp',
                                               if_else(grepl('rest', tmp.events$text), 'rest1', 
                                                       if_else(grepl('IntResp', tmp.events$text), 'IntResp','stim'))))
    
    # unique(tmp.events$screencontent)
    
    # create condition
    
    tmp.events$Condition<- if_else(grepl('IAPS', tmp.events$text), 'IAPS',
                                   if_else(grepl('Example', tmp.events$text), 'Practice',
                                           if_else(grepl('rest', tmp.events$text), 'Rest', NULL)))
    
    tmp.events$stim<- if_else(tmp.events$Condition == 'IAPS', sub(".*_ *(.*?) *jpg.*", "\\1", tmp.events$text),
                              if_else(tmp.events$Condition == 'Practice', sub(".*_ *(.*?) *jpg.*", "\\1", tmp.events$text), 'REST'))
    
    # substitute periods
    tmp.events$stim <- gsub('\\.', '.jpg', tmp.events$stim)
    
    # this is center trial numbers such that practice is below  1
    tmp.events$tNo<- if_else(tmp.events$Condition == 'Practice', (tmp.events$tNo)-6,
                             if_else(tmp.events$Condition == 'Rest',-7, tmp.events$tNo))
    
    # create trial number < 0 are practice trials
    tmp.events$tNo<- if_else(tmp.events$tNo> -1, tmp.events$tNo+1, tmp.events$tNo) # avoid zeros
    
    # remove rows with trial end
    tmp.events1 = subset(tmp.events, grepl('tStart',tmp.events$text))
 
  # remove NAS if present
    tmp.events1<- subset(tmp.events1, is.na(tmp.events1$tNo) == FALSE)
  
    # create some columns we need
    tmp.df$screencontent<- NA
    tmp.df$stim<- NA
    
    tmp.events1$tEnd<- if_else(tmp.events1$tNo == -7, tmp.events1$tStart+120, tmp.events1$tEnd)
    
    message(sprintf("subsetting eyetracking data"))
    
    # convert raw to double
    tmp.eyetr<-tmp.eyetr %>%
  mutate_if(is.raw, as.double)
    
    # e = 2
    for(e in 1:nrow(tmp.events1)) {
      
      # Subset the EyeTracking data based on start/end
      tmp.raw.trial = subset(tmp.eyetr, tmp.eyetr$time >= tmp.events1$tStart[e] & tmp.eyetr$time <= tmp.events1$tEnd[e])
      
      tmp.raw.trial$tNo = tmp.events1$tNo[e]
      
      tmp.raw.trial$Condition = tmp.events1$Condition[e]
      tmp.raw.trial$screencontent = tmp.events1$screencontent[e]
      tmp.raw.trial$stim = tmp.events1$stim[e]
      # tmp.raw.trial$stim = tmp.events1$[e]
      tmp.raw.trial$ssid = ssid
      tmp.raw.trial$text = tmp.events1$text[e]
      
      message(sprintf("binding tmp.df"))
      
      tmp.df= rbind(tmp.raw.trial, tmp.df)
    }
     message(sprintf("done binding"))
    
    # Arrange the dataframe by time
    tmp.df1<- tmp.df%>%
      arrange(time)
    
    # Save file for the task with subject name
    name = sprintf("ss%s_GPdata",ssid)
    message(sprintf("saving data"))
    write.csv(as.data.frame(tmp.df1), paste(name,".csv"))
    # note in newer versions of r write_CSV throws an error so use write.csv

    # write calibration file
    name2 = sprintf("ss%s_GPdata_cali", ssid)
    write.csv(as.data.frame(cali), paste(name2,".csv"))
    
    as
  }
  
  
  message("Processing Completed.")
  tmp.df1
}

# run function
tmp_full<- gp.extractor(hdf5FilesPath)

unique(tmp_full$ssid)
```



Now cleaning gaze 

```{r, cleaning}
# function to read all the csvs into one dataframe
# set directoty
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/Step1_GpExtractor_Output/356_357_611_616")

# reads all individual gaze exported files into one big file
read_plus <- function(flnm) {
  data.table::fread(flnm, select = c("session_id","event_id", "time", "left_gaze_x", "left_gaze_y","right_gaze_x", "right_gaze_y","left_pupil_measure1",
                                     "right_pupil_measure1","gsr", "gsrv", 'hr', "hrv", "hrp", "status", "tNo",  "Condition", "screencontent", "stim", "ssid", "text")) %>% 
    mutate(filename = flnm)
}

# read all clean data 

tmp.df2 <-
  list.files(pattern = "*.csv", 
             full.names = T) %>% 
  map_df(~read_plus(.))

# unique(tmp.df2$ssid)
# check if we have NAs in ssid column
table(is.na(tmp.df2$ssid))
head(tmp.df2)
# check we have all participants

tmp.df2<- subset(tmp.df2, !is.na(ssid))

unique(tmp.df2$ssid)
```



#####################################################################################
# gp preprocessing funtion, checks for losses, averages gaze, pupil and pixelate
#####################################################################################

```{r, gppreprocessing}
gp_preprocessing = function(tmp.df2) {
  
  message(sprintf("step1 left gaze validity"))
  
  # transform invalid gaze into NA based on validity codes
  # to do: link the conventions file
  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$status != '20', tmp.df2$left_gaze_x, NULL)
  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$status != '22', tmp.df2$left_gaze_x_cor, NULL)
  tmp.df2$left_gaze_y_cor<- if_else(tmp.df2$status != '20', tmp.df2$left_gaze_y, NULL)
  tmp.df2$left_gaze_y_cor<- if_else(tmp.df2$status != '22', tmp.df2$left_gaze_y_cor, NULL)
  
  message(sprintf("step2 right gaze validity"))
  
  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$status != '2', tmp.df2$right_gaze_x, NULL)
  #
  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$status != '22', tmp.df2$right_gaze_x_cor, NULL)
  tmp.df2$right_gaze_y_cor<- if_else(tmp.df2$status != '22', tmp.df2$right_gaze_y, NULL)
  tmp.df2$right_gaze_y_cor<- if_else(tmp.df2$status != '22', tmp.df2$right_gaze_y_cor, NULL)

  # pupil validity
  
  message(sprintf("step3 pupil validity"))
  tmp.df2$left_pupil_measure1<- if_else(tmp.df2$status != '20', tmp.df2$left_pupil_measure1, NULL)
  tmp.df2$left_pupil_measure1<- if_else(tmp.df2$status != '22', tmp.df2$left_pupil_measure1, NULL)
  
  tmp.df2$right_pupil_measure1<- if_else(tmp.df2$status != '2', tmp.df2$right_pupil_measure1, NULL)
  tmp.df2$right_pupil_measure1<- if_else(tmp.df2$status != '22', tmp.df2$right_pupil_measure1, NULL)
  table(is.na(tmp.df2$right_pupil_measure1))
  
  # check gazepoint out of bounds and repixelate 
  # (1920/2 = 960 by 1200/2 = 600. add half to normalised coordinates from psychopy)
  # update according to setup
  
  message(sprintf("step 4 cutting off screen in points and repixelate"))
  
  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$left_gaze_x_cor >= -960 & tmp.df2$left_gaze_x_cor <= 960, tmp.df2$left_gaze_x_cor, NULL)
  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$right_gaze_x_cor >= -960 & tmp.df2$right_gaze_x_cor <= 960, tmp.df2$right_gaze_x_cor, NULL)
  
  tmp.df2$left_gaze_y_cor<- if_else(tmp.df2$left_gaze_y_cor >= -600 & tmp.df2$left_gaze_y_cor <= 600, tmp.df2$left_gaze_y_cor, NULL)
  tmp.df2$right_gaze_y_cor<- if_else(tmp.df2$right_gaze_y_cor >= -600 & tmp.df2$right_gaze_y_cor <= 600, tmp.df2$right_gaze_y_cor, NULL)
  
  tmp.df2$left_gaze_x_cor_pix<- tmp.df2$left_gaze_x_cor+960
  tmp.df2$right_gaze_x_cor_pix<- tmp.df2$right_gaze_x_cor+960
  
  tmp.df2$left_gaze_y_cor_pix<- tmp.df2$left_gaze_y_cor+600
  tmp.df2$right_gaze_y_cor_pix<- tmp.df2$right_gaze_y_cor+600
  
  # is left or right an NA
  
  tmp.df2$left_na<- is.na(tmp.df2$left_gaze_x_cor) 
  tmp.df2$right_na<- is.na(tmp.df2$right_gaze_x_cor)
  tmp.df2$both_na<- if_else(tmp.df2$left_na == TRUE & tmp.df2$right_na == TRUE, TRUE, FALSE)
  
  message(sprintf("step5 gaze x  means"))
  
  tmp.df2$gaze_x_cor<-if_else(tmp.df2$left_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$right_gaze_x_cor,
                              if_else(tmp.df2$right_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$left_gaze_x_cor,
                                      ((tmp.df2$left_gaze_x_cor + tmp.df2$right_gaze_x_cor)/2)))
  message(sprintf("step6 gaze y means"))
  
  tmp.df2$gaze_y_cor<-if_else(tmp.df2$left_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$right_gaze_y_cor,
                              if_else(tmp.df2$right_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$left_gaze_y_cor,
                                      ((tmp.df2$left_gaze_y_cor + tmp.df2$right_gaze_y_cor)/2)))
  
  message(sprintf("step6 repixelate gaze means"))
  
  tmp.df2$gaze_x_cor_pix<- tmp.df2$gaze_x_cor + 960
  min(tmp.df2$gaze_x_cor_pix, na.rm = TRUE)
  
  tmp.df2$gaze_y_cor_pix<- tmp.df2$gaze_y_cor+600
  min(tmp.df2$gaze_y_cor_pix, na.rm = TRUE)
  
  # clean_pupil
  
  message(sprintf("cleaning pupil"))
  
  max(tmp.df2$left_pupil_measure1)
  
  tmp.df2$pupil<- if_else(tmp.df2$left_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$right_pupil_measure1,
                          if_else(tmp.df2$right_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$left_pupil_measure1,
                                  ((tmp.df2$left_pupil_measure1 + tmp.df2$right_pupil_measure1)/2)))
  
  # tmp.df2$trackloss<- if_else(tmp.df2$status > 0, TRUE, FALSE)
  tmp.df2$trialUnq<- paste(tmp.df2$tNo, paste(tmp.df2$screencontent, paste(tmp.df2$stim)))
  tmp.df2$distance = 630
  
  # min(tmp.df2$pupil, na.rm = TRUE)
  # max(tmp.df2$pupil, na.rm = TRUE)
  # colnames(tmp.df2)
  tmp.df2<- tmp.df2%>%
    arrange(time)
}

tmp.df2_processed<- gp_preprocessing(tmp.df2)
 colnames(tmp.df2) 
 
min(tmp.df2_processed$pupil, na.rm = TRUE)
range(tmp.df2_processed$gaze_y_cor_pix, na.rm = TRUE)
range(tmp.df2_processed$gaze_x_cor_pix, na.rm = TRUE) 

tmp.df2<- tmp.df2_processed
  
```


# for gaze parsing

```{r}

(sprintf("preparing for gazepath"))
  
colnames(tmp.df4)
  
  for_gazepath<- select(tmp.df4, c(2:15,17:26, 39:40,42:43))
  
  for_gazepath<- subset(for_gazepath, ssid!= 616)
  
  for_gazepath$screencontent[for_gazepath$screencontent == 'rest1']<- 'fixation'
  for_gazepath<- for_gazepath%>%
    arrange(ssid, time, tNo)
  
  colnames(for_gazepath)
  unique(for_gazepath$ssid)
  
  
  for_gazepath<- subset(for_gazepath, is.na(for_gazepath$time) == FALSE)
   # View(for_gazepath)
  
  for_gazepath$split_column<- paste0(for_gazepath$ssid, paste0(for_gazepath$screencontent))
  splitcol<- unique(for_gazepath$split_column)
  splitcol
  # ssid<- unique(for_gazepath$ssid)
  # ssid
  split_df = split(for_gazepath, list(for_gazepath$split_column))
  
  
  # setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/GP_IAPS_for_gazepath/346_355")
  
  setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/GP_IAPS_for_gazepath/356_357_611_615")
  
  (sprintf("writing for gazepath"))
  # ssid = split(for_gazepath, list(for_gazepath$ssid))
  # for (ssid in names(split_df)) {
    for (splitcol in names(split_df)) {
      # message( split_df[splitcol])
      write_csv(split_df[[splitcol]], paste0('gp_',paste0(splitcol),".csv"))
    }


```



# rezeroing times by trial, by participants

```{r}
tmp.df3 <- tmp.df2

# create start at every screen content
tmp.df3<- tmp.df3%>% 
  arrange(ssid, time, tNo)%>%
  group_by(ssid)%>%
  mutate(firststart = duplicated(trialUnq))

head(tmp.df3)

# make zero-times
tmp.df3$zero<- if_else(tmp.df3$firststart == FALSE, tmp.df3$time, NULL)

# fill in the zeros
tmp.df3<- tmp.df3%>%
  group_by(ssid, Condition, tNo)%>%
  # group_by(text)%>%
  fill(zero)

unique(tmp.df3$zero)

# rezero
tmp.df3<-tmp.df3%>%
  arrange(ssid, time, tNo)%>%
  group_by(ssid, tNo)%>%
  mutate(timerezero = time - zero)

min(tmp.df3$timerezero, na.rm = TRUE)
max(tmp.df3$timerezero, na.rm = TRUE) # max shoudl be around 120s for 2 minutes


# let's check to see if it looks fine
ggplot(subset(tmp.df3, tmp.df3$tNo == -1), aes(timerezero, gaze_x_cor_pix, colour = as.factor(ssid)))+
  geom_line()


ggplot(subset(tmp.df3, tmp.df3$tNo == -1), aes(timerezero, pupil, colour = as.factor(ssid)))+
  geom_line()

```

# create a new time rezero where before stim start, time is negative
```{r}
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, Condition, screencontent)%>%
  mutate(firststartSTIM = duplicated(tNo))

#this will create a time in the stim start which we can use to do the a second rezeroing
tmp.df3$zero_stim<- if_else(tmp.df3$firststartSTIM == FALSE & tmp.df3$screencontent == 'stim', tmp.df3$time, NULL)
   
    # fill down
tmp.df3<- tmp.df3%>%
      arrange(time)%>%
      group_by(tNo, ssid)%>%
      fill(zero_stim, .direction = c('updown'))

   tmp.df3$timerezero2<- tmp.df3$time-tmp.df3$zero_stim
   
   # check timerezero2
     range(tmp.df3$timerezero2, na.rm = TRUE)

# time 3 including rest
  # simply includes rest as is

tmp.df3$timerezero3<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$timerezero, tmp.df3$timerezero2)
min(tmp.df3$timerezero3, na.rm = TRUE)


# quick check that everything is fine

ggplot(subset(tmp.df3, tmp.df3$tNo == 27 ) , aes(x = timerezero3, y= pupil, colour = as.factor(ssid)))+
    geom_smooth()+
    # geom_()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)


```

# rest

```{r}
ggplot(subset(tmp.df3, tmp.df3$tNo == -7) , aes(x = timerezero3, y= pupil, colour = as.factor(ssid)))+
  # geom_point()
      geom_line() +
    # geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

```



to do
```{r}
install.packages("gazer")
library(gazer)

min(tmp.df3$pupil, na.rm = TRUE)
max(tmp.df3$pupil, na.rm = TRUE)

tmp.df3$pupil<- if_else(tmp.df3$pupil> 7.2, tmp.df3$pupil, NULL)

tmp.df3$pupil<- if_else(tmp.df3$pupil< 45, tmp.df3$pupil, NULL)

tmp.df3_backup <- tmp.df3


# note that smothing and interpolating is order dependent so order by ssid, trial and time
tmp.df3<- tmp.df3 %>%
  arrange(ssid, time,tNo)%>%
  group_by(ssid, trialUnq,tNo,screencontent) %>%
  mutate(extendpupil=gazer::extend_blinks(pupil, fillback=100, fillforward=100, hz=150))

min(tmp.df3$extendpupil, na.rm = TRUE)
max(tmp.df3$pupil, na.rm = TRUE)

# let's check

ggplot(subset(tmp.df3, tmp.df3$tNo == 3), aes(x = timerezero3, y= extendpupil , colour = as.factor(ssid)))+
      geom_line()
  # geom_line(aes(y = extendpupil), linetype = 'dashed', colour = 'red')

# Smooth and Interpolate
tmp.df3$subject<- tmp.df3$ssid
tmp.df3$trial <- tmp.df3$trialUnq

# min(pup_extend$pupil, na.rm = TRUE)
tmp.df3$extendpupil
# ?smooth_interpolate_pupil

# library(gazer)

?smooth_interpolate_pupil

# vert order dependent
tmp.df3 <- gazer::smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
                                    extendblinks=TRUE, step.first= 'smooth',
                                    maxgap=Inf, 
                                    filter = 'moving',
                                    type="linear", hz=150, n = 30)

# tmp.df3<- tmp.df3 %>%
#   group_by(ssid, trialUnq,tNo,screencontent) %>%
#   smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
#                                     extendblinks=TRUE, 
#                            step.first= 'smooth',
#                                     maxgap=10, 
#                                     filter = 'moving',
#                                     type="linear", hz=20, n = 10)
# 
# 
# tmp.df3<-
#   tmp.df3%>%
#   arrange(ssid,tNo,time)
#   # group_by(ssid, tNo, timerezero3)%>%
# 
# tmp.df3te<- tmp.df3 %>%
#   group_by(ssid, Condition,tNo,screencontent) %>%
#   smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
#                                     extendblinks=TRUE, 
#                            step.first= 'smooth',
#                                     maxgap=Inf, 
#                                     filter = 'moving',
#                                     type="linear", hz=100, n = 5)

min(tmp.df3$pup_interp, na.rm = TRUE)
max(tmp.df3$pup_interp, na.rm = TRUE)

subset(tmp.df3, tNo == 20 & ssid == 357)%>%
ggplot(aes(x = timerezero3, y= pup_interp))+
  geom_line()+
   geom_line(aes(y = extendpupil), color = 'red')+
  geom_line(aes(y = pupil), colour = 'gray')
  # facet_grid(~Condition)


subset(tmp.df3, tNo == -7 & ssid == 357)%>%
ggplot(aes(x = timerezero3, y= pupil))+
  geom_line()


subset(tmp.df3, tNo == 1)%>%
ggplot(aes(x = timerezero3, y= pup_interp))+
  geom_line()+
   # geom_line(aes(y = extendpupil), color = 'red')+
  # geom_line(aes(y = pup_interp), colour = 'gray')+
    facet_grid(~ssid)
  # facet_grid(~Condition)
```

process gazepath and ledalab



```{r}
tmp.df3$subject<- tmp.df3$ssid
tmp.df3$trial <- tmp.df3$trialUnq
tmp.df4<- select(tmp.df3, c("session_id", "event_id", "ssid", "subject", "text", "trial","trialUnq", "tNo", "Condition" ,"screencontent","stim",
                            "time", "timerezero", "timerezero2", "timerezero3", "status","filename",
                            "left_gaze_x_cor_pix","right_gaze_x_cor_pix","left_gaze_y_cor_pix","right_gaze_y_cor_pix",  "gaze_x_cor_pix",  "gaze_y_cor_pix",
                            "pupil",
                            "distance"))
head(tmp.df4)




tmp.df4$trackloss<- if_else(is.na(tmp.df4$gaze_x_cor_pix) == TRUE, 0, 
                         if_else(is.na(tmp.df4$gaze_y_cor_pix) == TRUE, 0, 1))
unique(tmp.df4$trackloss)

# compute proportion of lost data

tmp.df4$ssid
tmp.df4 <- tmp.df4 %>%
  group_by(ssid, tNo, trialUnq, text)%>%
  mutate(gaze_valid_prop = sum(trackloss)/n())%>%
  mutate(gaze_loss_prop = 1 - gaze_valid_prop)
  # mutate(hr_valid_prop = sum(hr_trackloss)/n())%>%
  # mutate(hr_loss_prop = 1 - hr_valid_prop)

# check to see this is right
ggplot(subset(tmp.df4, tmp.df3$ssid == 624) , aes(x = tNo, y= gaze_valid_prop))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = gaze_valid_prop), linetype = 'dashed', colour = 'green', size = 0.3)
   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
```


# for gaze parsing


```{r}
(sprintf("preparing for gazepath"))

colnames(tmp.df4)
  
  for_gazepath<- select(tmp.df4, c(2:15,17:28))
  
  # for_gazepath<- subset(for_gazepath, ssid!= 616)
  
  for_gazepath$screencontent[for_gazepath$screencontent == 'rest1']<- 'fixation'
  
  for_gazepath<- for_gazepath%>%
    arrange(ssid, time, tNo)
  
  colnames(for_gazepath)
  unique(for_gazepath$ssid)
  
  
  for_gazepath<- subset(for_gazepath, is.na(for_gazepath$time) == FALSE)
   # View(for_gazepath)
  
  for_gazepath$split_column<- paste0(for_gazepath$ssid, paste0(for_gazepath$screencontent))
  
  splitcol<- unique(for_gazepath$split_column)
  splitcol
  # ssid<- unique(for_gazepath$ssid)
  # ssid
  split_df = split(for_gazepath, list(for_gazepath$split_column))
  
  

  setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/GP_IAPS_for_gazepath/356_357_611_615")
  
  (sprintf("writing for gazepath"))
  # ssid = split(for_gazepath, list(for_gazepath$ssid))
  # for (ssid in names(split_df)) {
    for (splitcol in names(split_df)) {
      # message( split_df[splitcol])
      write_csv(split_df[[splitcol]], paste0('gp_',paste0(splitcol),".csv"))
    }

```
gazepath settings

left eye x coord: left_gaze_x_cor_pix
left eye y coord: left_gaze_y_cor_pix

didtance: distance (mm)

right eye x coord: right_gaze_x_cor_pix
right eye y coord: right_gaze_y_cor_pix
didtance: distance (mm)

trial index: trialnq


sample rate: 150
screen resolution height (pix): 1200
screen resolution width (pix): 1920

stimuli height (px): 768
stimuli width (px): 1024
variables to keep: trial unq

203
270

```{r}


install.packages('gazepath')
library(gazepath)
GUI()

```


