---
title: "intero_2022_23_OpenFaceprocesing"
author: "Helio"
date: "2023-02-27"
output: html_document
---

```{r setup, include=FALSE}


# Set working directory to the folder containing subfolders with CSV files
setwd("path/to/directory/")
setwd("~/Library/CloudStorage/GoogleDrive-helioclemente.c@gmail.com/My Drive/Papers 2022/InteroceptionStudy/InteroStudy2020/Data Collection 2019- 2020/2022/iaps/Preprocessed/faces/processed")

# Get a list of all CSV files within subfolders using list.files() and recursive = TRUE
file_list <- list.files(pattern = "\\.csv$", recursive = TRUE)


# Initialize an empty data frame to hold combined data
combined_data <- data.frame()

# Loop through each CSV file in the list and read it into a data frame using read.csv()

grepl("IAPSfix", file_list)
file_list[]
unique(file_list)

# set your working directory to the folder containing your CSV files
setwd("path/to/folder")

# get a list of all the CSV files in your folder and its subfolders
file_list <- list.files(pattern = "\\.csv$", recursive = TRUE, full.names = TRUE)

# read the CSV files into a list of data frames, and store the filename as a new column in each data frame
data_list <- lapply(file_list, function(file) {
  data <- read.csv(file)
  data$filename <- file
  data
})

# combine the data frames into a single data frame
dta_OF_combined <- do.call(rbind, data_list)
# View the resulting combined data frame
dta_OF_combined

unique(dta_OF_combined$filename)

write_rds(dta_OF_combined, "dta_OF_combined_all.rds")

colnames(dta_OF_combined)

dta_OF_combined_select<- dta_OF_combined[,c(1:5, 680:715)]

colnames(dta_OF_combined_select)

# create variables
dta_OF_combined_select$ssid<- substr(dta_OF_combined_select$filename, 1,3)

unique(dta_OF_combined_select$ssid)

dta_OF_combined_select<- dta_OF_combined_select%>%
  subset(ssid != "IAP")

dta_OF_combined_select$screencontent<- if_else(grepl("IAPSfix",dta_OF_combined_select$filename), "fixation", "stimuli")

unique(dta_OF_combined_select$screencontent)

dta_OF_combined_select$practice_stim <- if_else(grepl("Example",dta_OF_combined_select$filename), "practice", "trial")

unique(dta_OF_combined_select$practice_stim)
unique(dta_OF_combined_select$filename)

dta_OF_combined_select$filename2<- substr(dta_OF_combined_select$filename,5,200)
dta_OF_combined_select$filename2<- str_remove(dta_OF_combined_select$filename2, "IAPS|fix")
unique(dta_OF_combined_select$filename2)

dta_OF_combined_select$filename2<- substr(dta_OF_combined_select$filename2,6,200)
dta_OF_combined_select$filename2
dta_OF_combined_select$stimIAPS <- substr(dta_OF_combined_select$filename2,1,8)

dta_OF_combined_select$filename2



# [1] "world"
# dta_OF_combined_select$trialIAPS.thisTrialN<- str_remove(sub(".*__", "", dta_OF_combined_select$filename2), ".csv")
# dta_OF_combined_select$trialIAPS.thisTrialN
# unique(dta_OF_combined_select$trialIAPS.thisTrialN)
# doesn't work that we;;

# dta_OF_combined_select$trialIAPS.thisTrialN<- NULL
dta_OF_combined_select_stimuli<- subset(dta_OF_combined_select, screencontent == "stimuli")

colnames(dta_OF_combined_select_stimuli)


dta_OF_combined_select_stimuli_agg<- dta_OF_combined_select_stimuli%>%
  group_by(ssid, practice_stim,stimIAPS)%>%
  summarise_if(is.numeric, mean, na.rm = T)

colnames(as.data.frame(dta_OF_combined_select_stimuli_agg))
length(colnames(dta_OF_combined_select_stimuli_agg))

tmp_AUnames

tmp_AUnames<- c("ssid" ,         
                "practice_stim", 
                "stimIAPS"   ,   
                "frame"    ,     
                "face_id"      , 
                "timestamp"   ,  
                "confidence" ,   
                "success",
 "AU01_r_Inner_brow_raiser",   
 "AU02_r_Outer_brow_raiser",   
 "AU04_r_Brow_lowerer",       
"AU05_r_Upper_lid_raiser",    
"AU06_r_Cheek_raiser",        
"AU07_r_Lid_tightener",       
"AU09_r_Nose_wrinkler",      
 "AU10_r_Upper_lip_raiser",    
"AU12_r_Lip_corner_puller",   
"AU14_r_Dimpler",             
"AU15_r_Lip_corner_depressor",
 "AU17_r_Chin_raiser",         
"AU20_r_Lip_stretcher",       
"AU23_r_Lip_tightener",      
"AU25_r_Lips_part",          
"AU26_r_Jaw_drop",            
"AU45_r_Blink",               
"AU01_c_Inner_brow_raiser",   
"AU02_c_Outer_brow_raiser",  
"AU04_c_Brow_lowerer",        
"AU05_c_Upper_lid_raiser",    
"AU06_c_Cheek_raiser",        
"AU07_c_Lid_tightener",      
"AU09_c_Nose_wrinkler",      
"AU10_c_Upper_lip_raiser",    
"AU12_c_Lip_corner_puller",   
"AU14_c_Dimpler",            
 "AU15_c_Lip_corner_depressor",
"AU17_c_Chin_raiser",        
"AU20_c_Lip_stretcher",       
"AU23_c_Lip_tightener",      
"AU25_c_Lips_part",          
"AU26_c_Jaw_drop",    
"AU28_c_Lip_suck",    
"AU45_c_Blink")
tmp_AUnames

dta_OF_combined_select_stimuli_agg<- dta_OF_combined_select_stimuli_agg2
dta_OF_combined_select_stimuli_agg2<- dta_OF_combined_select_stimuli_agg
colnames(dta_OF_combined_select_stimuli_agg)<- tmp_AUnames

dta_OF_combined_select_stimuli_agg
# AU names

# merge with the rest of the data
dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze

dta_OF_combined_select_stimuli_agg$stimIAPS<-as.character(dta_OF_combined_select_stimuli_agg$stimIAPS)
dta_OF_combined_select_stimuli_agg$ssid<- as.double(dta_OF_combined_select_stimuli_agg$ssid)
unique(dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze$stimIAPS)

unique(str_replace_all(dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze$stimIAPS, " ",""))

dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze$stimIAPS<-str_replace_all(dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze$stimIAPS, " ","")


dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze$stimIAPS


dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze_OF<-
left_join(dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze,dta_OF_combined_select_stimuli_agg)



colnames(dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze_OF)

dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze_OF$self_valence_2.response
# 
# dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze_OF$valence_response<- if_else(is.na(dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze_OF$self_valence_2.response) == TRUE,                                                                  dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze_OF$self_valence_4.response,
#                                                                                     dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze_OF$self_valence_2.response)
# 
# dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze_OF$arousal_response <-
#   if_else(is.na(dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze_OF$Self_intensity_2.response) == TRUE, as.numeric(dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze_OF$Self_intensity_3.response),                                                                        as.numeric(dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze_OF$Self_intensity_2.response))


colnames(dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze_OF)

dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze_OF$valence
dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze_OF


dta_all_merged_sel<- dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze_OF[,c(26,2:6,31,33:41,45:47,17:19,21:22,25,27:28,52:63,90:102,109:143)]

# missing alexiuthymia
colnames(dta_all_merged_sel)
dta_bhv_quest1.1_with_fix_resp_arranged_scr_stim_gaze_OF

dta_all_merged_sel

# fto do ix questionnaire merging earlier - acidentally merged only AQ
dta_quests

left_join(dta_beh1,dta_quests)

unique(dta_all_merged_sel$completion_code)
unique(dta_beh1$completion_code)
dta_quests$completion_code

length(unique(dta_all_merged_sel$ssid))

tmp_id_test<-
dta_all_merged_sel%>%
  group_by(ssid,completion_code)%>%
  summarise_at("AQ", mean, na.rm = T)

tmp_id_test$completion_code<- str_remove(tmp_id_test$completion_code,"\r")

dta_all_merged_sel$completion_code<- str_remove(dta_all_merged_sel$completion_code,"\r")
unique(str_remove(dta_all_merged_sel$completion_code,"\r"))
dta_quests

dta_quests$completion_code
dta_all_merged_sel$participant_private_id
unique(dta_quests$completion_code)
unique(dta_all_merged_sel$completion_code)
dta_all_merged_sel2<-left_join(dta_all_merged_sel, dta_quests,
                               
                               Joining, by = c("completion_code"))

dta_all_merged_sel2.1<- subset(dta_all_merged_sel2, !is.na(dta_all_merged_sel2$TotalAlexScore))

colnames(dta_all_merged_sel2)

colnames(dta_all_merged_sel2)
dta_all_merged_sel3<- dta_all_merged_sel2.1[,c(1:19,88:99,105:108, 20:87)]

dta_all_merged_sel3.1<- subset(dta_all_merged_sel3, dta_all_merged_sel3$happiness_3.response != "None")


dta_all_merged_sel3.1<- dta_all_merged_sel3.1 %>%
  mutate(TAS_med_spli = if_else(TotalAlexScore> median(TotalAlexScore,na.rm = T), "high", "low"),
         AQ_med_spli = if_else(AQ.x> median(AQ.x,na.rm = T), "high", "low")
         
         )

colnames(dta_all_merged_sel3.1)

dta_all_merged_sel3.1%>%
  data.table::dcast(...~stimIAPS, mean, value.var = c(36:103))

dta_all_merged_sel3.1

# drop latency

write_csv(dta_all_merged_sel3.1, "dta_all_merged_sel3.1.csv")

FactoMineR
install.packages("Factoshiny")
library(Factoshiny)

dta_all_merged_sel3.1$ha
Factoshiny::MFAshiny(dta_all_merged_sel3.1)


colnames(dta_all_merged_sel3.1)
dta_all_merged_sel3.1<- dta_all_merged_sel3.1%>%
  mutate(happiness_3.response = as.numeric(happiness_3.response),
         sadness_3.response = as.numeric(sadness_3.response),
           sadness_3.response = as.numeric(sadness_3.response),
           surprise_3.response = as.numeric(surprise_3.response),
          disgust_3.response = as.numeric(disgust_3.response),
          fear_3.response = as.numeric(fear_3.response))


table(is.na(dta_all_merged_sel3.1$happiness_3.response))

table(is.na(dta_all_merged_sel3.1$fear_3.response))

dta_all_merged_sel3.1$condition

dta_all_merged_sel3.1_trial<-dta_all_merged_sel3.1%>%
  subset(condition == "IAPS")


dta_all_merged_sel3.1_trial

table(is.na(dta_all_merged_sel3.1_trial$fear_3.response))
table(is.na(dta_all_merged_sel3.1_trial$fear_3.response))
table(is.na(dta_all_merged_sel3.1_trial$disgust_3.response))

write_csv(dta_all_merged_sel3.1_trial, "dta_all_merged_sel3.1_trial.csv")

# include anger
dta_beh$anger_3.response

dta_beh$ssid<- dta_beh$Participant

dta_beh$stimIAPS
dta_beh$condition

dta_beh$anger_3.response<- as.numeric(dta_beh$anger_3.response)
dta_beh$anger_3.response

dta_anger<-dta_beh%>%
  group_by(ssid, stimIAPS,condition)%>%
  summarise_at(c("anger_3.response"), mean, na.rm = T)%>%
  subset(!is.na(anger_3.response
))
  
dta_anger_trial<- subset(dta_anger, condition == "IAPS")


dta_anger_trial

dta_anger_trial$stimIAPS<- str_remove_all(dta_anger_trial$stimIAPS, " ")
unique(dta_anger_trial$stimIAPS)
dta_all_merged_sel3.1_trial<- left_join(dta_all_merged_sel3.1_trial, dta_anger_trial)

# load pupil
library(readr)
dta_pupil_stim_agg <- read_csv("~/Library/CloudStorage/GoogleDrive-helioclemente.c@gmail.com/My Drive/Papers 2022/InteroceptionStudy/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/2022_2023_Analyses/Data/dta_pupil_stim_agg.csv")
View(dta_pupil_stim_agg)

dta_pupil_stim_agg$tNo
dta_pupil_stim_agg$text

unique(substr(dta_pupil_stim_agg$text, 13,20))
dta_pupil_stim_agg$stimIAPS<- substr(dta_pupil_stim_agg$text, 13,20)

dta_all_merged_sel3.1_trial<- left_join(dta_all_merged_sel3.1_trial, dta_pupil_stim_agg)
dta_pupil_stim_agg
dta_all_merged_sel3.1_trial


dta_all_merged_sel3.1_trial$AQ_med_spli

dta_all_merged_sel3.1_trial$TAS_med_spli <- if_else(dta_all_merged_sel3.1_trial$TotalAlexScore > median(dta_all_merged_sel3.1_trial$TotalAlexScore), "high", "low")

dta_all_merged_sel3.1_trial$AQ_med_spli <- if_else(dta_all_merged_sel3.1_trial$AQ.x > median(dta_all_merged_sel3.1_trial$AQ.x, na.rm = T), "high", "low")


dta_all_merged_sel3.1_trial$AQ_mean_filled<- if_else(is.na(dta_all_merged_sel3.1_trial$AQ.x), mean(dta_all_merged_sel3.1_trial$AQ.x, na.rm = T), dta_all_merged_sel3.1_trial$AQ.x)


dta_all_merged_sel3.1_trial$AQ_med_spli <- if_else(dta_all_merged_sel3.1_trial$AQ_mean_filled > median(dta_all_merged_sel3.1_trial$AQ_mean_filled, na.rm = T), "high", "low")


unique(dta_all_merged_sel3.1_trial$TAS_med_spli)

unique(dta_all_merged_sel3.1_trial$AQ_med_spli)
                                                    
```

MFA

```{r}
dta_all_merged_sel3.1_trial
Factoshiny::MFAshiny(dta_all_merged_sel3.1_trial)

dta_all_merged_sel3.1_trial$ssid<- as.factor(as.character(dta_all_merged_sel3.1_trial$ssid))

?MFA()

Factoshiny::PCAshiny(dta_all_merged_sel3.1_trial)


clustering_new_pre_PCA_2

colnames(dta_all_merged_sel3.1_trial)

dta_all_merged_sel3.1_trial[,c(1,3,42,43,36:40,46:50, 56:68,69:85)]

length(c("n", "s", "s", 
                        rep("s",5),
                        # "s","s","s","s","s",]
                        rep("s",12),
                        rep("s",16)
                        
                        # "s","s","s","s","s","s","s","s","s","s","s","s",
                        
                        
                        ))

colnames(dta_all_merged_sel3.1_trial)
dta_all_merged_sel3.1_trial_1<-
dta_all_merged_sel3.1_trial[,c(1,3, 104:105, 42,43,36:40,106,46:50, 56:68,69:85,114,117)]

colnames(dta_all_merged_sel3.1_trial_1)

newDF <- dta_all_merged_sel3.1_trial_1[,c("happiness_3.response","fear_3.response","anger_3.response","sadness_3.response","disgust_3.response","surprise_3.response","valence","arousal")]
res.MFA<-MFA(newDF,group=c(6,1,1), type=c("s","s","s"),name.group=c("emotioncat","valence","arousal"),graph=FALSE)
plot.MFA(res.MFA, choix="ind",lab.par=FALSE,title="Individual factor map")
plot.MFA(res.MFA, choix="var",habillage='group',title="Correlation circle")
plot.MFA(res.MFA, choix="group")
plot.MFA(res.MFA, choix="axes",habillage='group')

MFA(dta_all_merged_sel3.1_trial_1, 
               group = c(2,1,1,6,5,13,17,2), 
               type = c("n", 
                        "s", 
                        "s", 
                        rep("s",6),
                        rep("s",5),
                       
                        # "s","s","s","s","s",]
                        rep("s",13),
                        rep("s",17),
                        rep("s",2)),
                        
                        # "s","s","s","s","s","s","s","s","s","s","s","s",
                        
                        
                        # ),
               name.group = c("pp_stim_cat","valence","arousal", "emotionratings",
                              "SCR", "gaze", "face", "pupil"),
               num.group.sup = c(1,2),
               graph = TRUE)

# 
newDF <- dta_all_merged_sel3.1_trial_1[,c("happiness_3.response","fear_3.response","anger_3.response","sadness_3.response","disgust_3.response","surprise_3.response","valence","arousal","cda_scr_mu_s","cda_tonic_mu_s","cda_iscr_mu_sxs","cda_amp_sum_mu_s","cda_phasic_max_mu_s")]
res.MFA<-MFA(newDF,group=c(6,1,1,5), type=c("s","s","s","s"),name.group=c("emotioncat","valence","arousal","scr"),graph=FALSE)
plot.MFA(res.MFA, choix="ind",lab.par=FALSE,title="Individual factor map")
plot.MFA(res.MFA, choix="var",habillage='group',title="Correlation circle")
plot.MFA(res.MFA, choix="group")
plot.MFA(res.MFA, choix="axes",habillage='group')



newDF <- dta_all_merged_sel3.1_trial_1[,c("happiness_3.response","fear_3.response","anger_3.response","sadness_3.response","disgust_3.response","surprise_3.response","valence","arousal","cda_scr_mu_s","cda_tonic_mu_s","cda_iscr_mu_sxs","cda_amp_sum_mu_s","cda_phasic_max_mu_s","mean_x","mean_y","fix_Dur","fix_count","fix_Dur_sum","SacDur","SacAmpSac","Sac_count","Sac_Dur_sum")]
res.MFA<-MFA(newDF,group=c(6,1,1,5,9), type=c("s","s","s","s","s"),name.group=c("emotioncat","valence","arousal","scr","gaze"),graph=FALSE)
plot.MFA(res.MFA, choix="ind",lab.par=FALSE,title="Individual factor map")
plot.MFA(res.MFA, choix="var",habillage='group',title="Correlation circle")
plot.MFA(res.MFA, choix="group")
plot.MFA(res.MFA, choix="axes",habillage='group')


newDF <- dta_all_merged_sel3.1_trial_1[,c("happiness_3.response","fear_3.response","anger_3.response","sadness_3.response","disgust_3.response","surprise_3.response","valence","arousal","cda_scr_mu_s","cda_tonic_mu_s","cda_iscr_mu_sxs","cda_amp_sum_mu_s","cda_phasic_max_mu_s","mean_x","mean_y","fix_Dur","fix_count","fix_Dur_sum","SacDur","SacAmpSac","Sac_count","Sac_Dur_sum","AU45_r_Blink","AU14_r_Dimpler","AU26_r_Jaw_drop","AU25_r_Lips_part","AU17_r_Chin_raiser","AU04_r_Brow_lowerer","AU06_r_Cheek_raiser","AU07_r_Lid_tightener","AU09_r_Nose_wrinkler","AU20_r_Lip_stretcher","AU23_r_Lip_tightener","AU05_r_Upper_lid_raiser","AU10_r_Upper_lip_raiser","AU01_r_Inner_brow_raiser","AU02_r_Outer_brow_raiser","AU12_r_Lip_corner_puller","AU15_r_Lip_corner_depressor")]
res.MFA<-MFA(newDF,group=c(6,1,1,5,9,17), type=c("s","s","s","s","s","s"),name.group=c("emotioncat","valence","arousal","scr","gaze","face"),graph=FALSE)
plot.MFA(res.MFA, choix="ind",lab.par=FALSE,title="Individual factor map")
plot.MFA(res.MFA, choix="var",habillage='group',title="Correlation circle")
plot.MFA(res.MFA, choix="group")
plot.MFA(res.MFA, choix="axes",habillage='group')


newDF <- dta_all_merged_sel3.1_trial_1[,c("happiness_3.response","fear_3.response","anger_3.response","sadness_3.response","disgust_3.response","surprise_3.response","valence","arousal","cda_scr_mu_s","cda_tonic_mu_s","cda_iscr_mu_sxs","cda_amp_sum_mu_s","cda_phasic_max_mu_s","mean_x","mean_y","fix_Dur","fix_count","fix_Dur_sum","SacDur","SacAmpSac","Sac_count","Sac_Dur_sum","AU45_r_Blink","AU14_r_Dimpler","AU26_r_Jaw_drop","AU25_r_Lips_part","AU17_r_Chin_raiser","AU04_r_Brow_lowerer","AU06_r_Cheek_raiser","AU07_r_Lid_tightener","AU09_r_Nose_wrinkler","AU20_r_Lip_stretcher","AU23_r_Lip_tightener","AU05_r_Upper_lid_raiser","AU10_r_Upper_lip_raiser","AU01_r_Inner_brow_raiser","AU02_r_Outer_brow_raiser","AU12_r_Lip_corner_puller","AU15_r_Lip_corner_depressor","pupil","pupil_speed")]
res.MFA<-MFA(newDF,group=c(6,1,1,5,9,17,2), type=c("s","s","s","s","s","s","s"),name.group=c("emotioncat","valence","arousal","scr","gaze","face","pupil"),graph=FALSE)
plot.MFA(res.MFA, choix="ind",lab.par=FALSE,title="Individual factor map")
plot.MFA(res.MFA, choix="var",habillage='group',title="Correlation circle")
plot.MFA(res.MFA, choix="group")
plot.MFA(res.MFA, choix="axes",habillage='group')

```



```{r}
Show graphs options
Perform clustering after leaving MFA app?
Get the MFA code
Creation of groups
Graphs
Values
Automatic description of axes
Summary of dataset
Data


```


```{r}
library(factoextra)

library(FactoMineR)
library(FactoInvestigate)
# install.packages("Factoshiny")
library(Factoshiny)
dta_all_merged_sel3.1_trial_1

newDF <- dta_all_merged_sel3.1_trial_1[,c("happiness_3.response","fear_3.response","anger_3.response","sadness_3.response","disgust_3.response","surprise_3.response","valence","arousal","cda_scr_mu_s","cda_tonic_mu_s","cda_iscr_mu_sxs","cda_amp_sum_mu_s","cda_phasic_max_mu_s","mean_x","mean_y","fix_Dur","fix_count","fix_Dur_sum","SacDur","SacAmpSac","Sac_count","Sac_Dur_sum","AU45_r_Blink","AU14_r_Dimpler","AU26_r_Jaw_drop","AU25_r_Lips_part","AU17_r_Chin_raiser","AU04_r_Brow_lowerer","AU06_r_Cheek_raiser","AU07_r_Lid_tightener","AU09_r_Nose_wrinkler","AU20_r_Lip_stretcher","AU23_r_Lip_tightener","AU05_r_Upper_lid_raiser","AU10_r_Upper_lip_raiser","AU01_r_Inner_brow_raiser","AU02_r_Outer_brow_raiser","AU12_r_Lip_corner_puller","AU15_r_Lip_corner_depressor","pupil","pupil_speed","TAS_med_spli", "AQ_med_spli" )]

res.MFA<-MFA(newDF,group=c(6,1,1,5,9,17,2,1,1), type=c("s","s","s","s","s","s","s","n","n"),
             name.group=c("emotioncat","valence","arousal","scr","gaze","face","pupil","TASMed", "AQMed"),
             num.group.sup=c(8,9),
             graph=FALSE)

MFAshiny(newDF)


plot.MFA(res.MFA, choix="ind",lab.par=FALSE,title="Individual factor map")
plot.MFA(res.MFA, choix="var",habillage='group',title="Correlation circle")
plot.MFA(res.MFA, choix="group")
plot.MFA(res.MFA, choix="axes",habillage='group')

write_csv(dta_all_merged_sel3.1_trial_1, "dta_all_merged_sel3.1_trial_1.csv")

# about the heart rate

```



newDF <- newDF[,c("happiness_3.response","fear_3.response","anger_3.response","sadness_3.response","disgust_3.response","surprise_3.response","valence","arousal","cda_scr_mu_s","cda_phasic_max_mu_s","cda_iscr_mu_sxs","cda_amp_sum_mu_s","cda_tonic_mu_s","mean_x","mean_y","fix_Dur_sum","fix_count","fix_Dur","SacDur","SacAmpSac","Sac_count","Sac_Dur_sum","AU45_r_Blink","AU14_r_Dimpler","AU26_r_Jaw_drop","AU25_r_Lips_part","AU17_r_Chin_raiser","AU04_r_Brow_lowerer","AU06_r_Cheek_raiser","AU07_r_Lid_tightener","AU09_r_Nose_wrinkler","AU20_r_Lip_stretcher","AU23_r_Lip_tightener","AU05_r_Upper_lid_raiser","AU10_r_Upper_lip_raiser","AU01_r_Inner_brow_raiser","AU02_r_Outer_brow_raiser","AU12_r_Lip_corner_puller","AU15_r_Lip_corner_depressor","TAS_med_spli")]
res.MFA<-MFA(newDF,group=c(6,1,1,5,9,17,1), type=c("s","s","s","s","s","s","n"),name.group=c("emotion","valence","arousal","SCR","gaze","face","TASMed"),graph=FALSE)
plot.MFA(res.MFA, choix="ind",lab.par=FALSE,title="Individual factor map")
plot.MFA(res.MFA, choix="var",habillage='group',title="Correlation circle")
plot.MFA(res.MFA, choix="group")
plot.MFA(res.MFA, choix="axes",habillage='group')


```{r}
newDF1 <- newDF[,c("happiness_3.response","fear_3.response","anger_3.response","sadness_3.response","disgust_3.response","surprise_3.response","valence","arousal","cda_scr_mu_s","cda_phasic_max_mu_s","cda_iscr_mu_sxs","cda_amp_sum_mu_s","cda_tonic_mu_s","mean_x","mean_y","fix_Dur_sum","fix_count","fix_Dur","SacDur","SacAmpSac","Sac_count","Sac_Dur_sum","AU45_r_Blink","AU14_r_Dimpler","AU26_r_Jaw_drop","AU25_r_Lips_part","AU17_r_Chin_raiser","AU04_r_Brow_lowerer","AU06_r_Cheek_raiser","AU07_r_Lid_tightener","AU09_r_Nose_wrinkler","AU20_r_Lip_stretcher","AU23_r_Lip_tightener","AU05_r_Upper_lid_raiser","AU10_r_Upper_lip_raiser","AU01_r_Inner_brow_raiser","AU02_r_Outer_brow_raiser","AU12_r_Lip_corner_puller","AU15_r_Lip_corner_depressor","TAS_med_spli","AQ_med_spli")]


dfcompleted <- missMDA::imputeMFA(newDF1, ncp=2,group=c(6,1,1,5,9,17,1,1), type=c("s","s","s","s","s","s","n","n"))


res.MFA<-MFA(newDF1,tab.comp=dfcompleted,
             group=c(6,1,1,5,9,17,1,1),
             type=c("s","s","s","s","s","s","n","n"),
             name.group=c("emotion","valence","arousal","SCR","gaze","face","TASMed","AQMed"),graph=FALSE)

plot.MFA(res.MFA, choix="ind",lab.par=FALSE,invisible= 'quali.sup',habillage='TAS_med_spli',title="Individual factor map")
plot.MFA(res.MFA, choix="var",habillage='group',title="Correlation circle")
plot.MFA(res.MFA, choix="group")
plot.MFA(res.MFA, choix="axes",habillage='group')


# store dimensions
res.MFA$quanti.var

res.MFA$global.pca$quali.sup
res.MFA$global.pca$ind


newDF1$DIM1<- res.MFA$ind$coord[,1]
newDF1$DIM2<- res.MFA$ind$coord[,2]

dta_all_merged_sel3.1_trial$DIM3<- res.MFA$ind$coord[,2]

dta_all_merged_sel3.1_trial
dta_all_merged_sel3.1_trial$DIM1<- newDF1$DIM1
dta_all_merged_sel3.1_trial$DIM2<- newDF1$DIM2
dta_all_merged_sel3.1_trial$DIM3<- newDF1$DIM3

newDF1$ssid<- newDF1

dta_all_merged_sel3.1_trial_1

write_csv(dta_all_merged_sel3.1_trial, "dta_all_merged_sel3.1_trial.csv")

dta_all_merged_sel3.1_trial

write_c

```
