---
title: "Intero_2022_23_SCRprocess"
author: "Helio"
date: "2023-02-19"
output: html_document
---

<!-- to do -->
notes from eliza
Files have occasional random extra events - the labels on these are not given to any actual stimuli so should be easy to filter out - (on inspection ive seen 2,8 and 97 but there may be more) . There are very occasional missing triggers too, probably nothing to be done about that

There are duplicate events in 371, just get rid of the ones that say 2 in event.nid/event name


```{r}
setwd("~/Library/CloudStorage/GoogleDrive-helioclemente.c@gmail.com/My Drive/Papers 2022/InteroceptionStudy/InteroStudy2020/Data Collection 2019- 2020/2022/iaps/Preprocessed/Ledalab output")
dta_bhv_quest
colnames(dta_bhv_quest)

# import
tmp_files <- list.files(pattern = ".xls")


# Load necessary packages
library(readxl)
library(purrr)

# Set the path to the folder containing the xls files
tmp_path <- getwd()

# Get the list of all xls files in the folder
tmp_file_list <- list.files(tmp_path, pattern = "\\.xls$", full.names = TRUE)

# Read in all xls files and store them as a list of data frames
df_list <- map(tmp_file_list,~ read_excel(.x, sheet = 2))

# Add a new column to each data frame in the list containing the filename
df_list <- map2(df_list, tmp_file_list, ~mutate(.x, filename = .y))

# Combine all data frames in the list into a single dataframe
combined_df <- do.call(rbind, df_list)

dta_leda_bio<- combined_df

unique(dta_leda_bio$Event.NID)

unique(dta_leda_bio$Event.Name)

unique(dta_leda_bio$Event.Nr)

dta_leda_bio%>%
  group_by(filename)%>%
  table()

table(dta_leda_bio$filename)

dta_leda_bio<- dta_leda_bio%>%
  janitor::clean_names()



```

Journals
```{r}
# load journals


# Set the directory where the XLS files are located
setwd("path/to/xls/files")

# Create a function to read XLS files and add filename as a column
read_xls_file <- function(file) {
  # Read the XLS file, skip the first row, and convert it to a dataframe
  data <- read_excel(file, skip = 1)
  # Add a column with the filename
  data$filename <- basename(file)
  return(data)
}


# Get a list of all XLS files in the directory

# Get a list of all XLS files in the directory
# for some reasons there re problems with xls file in r
# seems to be related to https://stackoverflow.com/questions/28325744/r-xlsx-package-error
tmp_files <- list.files(pattern = "*.xlsx")

# Read all XLS files into a list of dataframes
dta_journal_list <- map(tmp_files, read_xls_file)

# Combine all dataframes into a single dataframe


# dta_journal <- bind_rows(dta_journal_list, coerce = TRUE)
dta_journal<- rbindlist(dta_journal_list) # this coerces regardless of type

dta_journal<- dta_journal%>%
  janitor::clean_names()
```


Now clean the nuisance

<!-- to do -->
notes from eliza
Files have occasional random extra events - the labels on these are not given to any actual stimuli so should be easy to filter out - (on inspection ive seen 2,8 and 97 but there may be more) . There are very occasional missing triggers too, probably nothing to be done about that

There are duplicate events in 371, just get rid of the ones that say 2 in event.nid/event name

```{r}
dta_journal$ssid<- substr(dta_journal$filename,1,3)
table(dta_journal$ssid)
table(dta_leda_bio$ssid)
dta_leda_bio$event_nr


range(dta_journal$index+1, na.rm = T)
range(dta_leda_bio_nid1$event_nr+1, na.rm = T)
tmp_bogus<- subset(dta_leda_bio_nid1, dta_leda_bio_nid1$event_nr>229)
dta_leda_bio_nid1_below229 <- subset(dta_leda_bio_nid1, as.numeric(dta_leda_bio_nid1$event_nr)<=229)


unique(dta_leda_bio_nid1_below229$event_nid)
# unique(dta_leda_bio_nid1_below229$)

dta_leda_bio_nid1_below229<-dta_leda_bio_nid1_below229%>%
  group_by(ssid)%>%
  mutate(event_nr_new = 1:n())


dta_journal$index_1<- dta_journal$index+1

table(dta_leda_bio_nid1$ssid)
table(dta_journal$ssid)
range(dta_journal$index+1, na.rm = T)
range(dta_leda_bio_nid1$event_nr+1, na.rm = T)

tmp_370<- dta_journal_1%>%subset(ssid == "370")
tmp_370_bioleda<- dta_leda_bio%>%subset(ssid == "370")
tmp_370$new_index

tmp_370_bioleda$event_nr



```


```{r}
table(dta_leda_bio_nid1_below229$ssid)
table(dta_journal$ssid)

dta_journal$new_index<-dta_journal$index_1

unique(dta_journal$label)
left_join()
dta_leda_bio_nid1_below229


tmp_jounal<- 
dta_journal%>%
  # subset(ssid == "359")%>%
  mutate(trigger_label = as.numeric(label))%>%
  subset(!is.na(label))
  # subset(trigger_label!= 1)%>%
  #  subset(trigger_label!= 2)%>%
  # subset(trigger_label!= 8)%>% 
  #  subset(trigger_label!= 97)%>%
  #  subset(trigger_label!= 98)%>%
    group_by(ssid)
  # mutate(diff_label = trigger_label -lead(trigger_label))%>%

  # mutate(remove_dup = if_else(trigger_label == 103 & diff_label !=2, "remove","keep")) %>%
  # mutate(remove_dup = if_else(is.na(remove_dup),"keep",remove_dup))%>%

# %>%  
  subset(remove_dup == "keep")
  # if we don't have 103 before 101 = 

table(dta_leda_bio_nid1_below229$ssid)

unique(dta_leda_bio_nid1_below229$event_nr)

unique(tmp_jounal$index)
table(tmp_jounal$ssid)


# tmp_jounal$time_sec<- substr(tmp_jounal)


tmp_jounal1<- tmp_jounal%>%
    mutate(time_sec = str_remove(time," sec"))%>%
mutate_at(c('index', 'time_sec','ssid'), as.numeric)%>%

  arrange(ssid, index)%>%
  group_by(ssid)%>%
  subset(!is.na(date_created))%>%
  mutate(new_index = 1:n())%>%
  mutate(nrows = n())

table(dta_leda_bio_nid1$ssid)
# table(tmp_jounal$ssid)
table(tmp_jounal1$ssid)
# missing from bio 362,373
tmp_sid<-tmp_jounal1%>%subset(ssid == "360")
tmp_sid_bio<-dta_leda_bio_nid1%>%subset(ssid == "360")

tmp_sid_bio$event_nr
tmp_sid$new_index
tmp_sid$trigger_label
sort(tmp_sid$trigger_label)
# 
tmp_jounal2<- tmp_jounal1%>%
  subset(as.numeric(trigger_label)!=8)%>% # 359
    subset(as.numeric(trigger_label)!=2)%>% # 359
  # 360
 mutate(new_index = 1:n())%>%
  mutate(nrows = n())
tmp_sid_journal$ssid

tmp_sid_journal$new_index
tmp_sid_bio<-tmp_jounal2%>%subset(ssid == "360")
# 8 for 359
length(tmp_sid_bio$trigger_label)
sort(tmp_sid_bio$trigger_label)

table(dta_leda_bio_nid1$ssid)
# table(dta_journal$ssid)
# table(tmp_jounal1$ssid)
table(tmp_jounal2$ssid)

# run manually
# 362,373

events_362<-tmp_jounal2%>%
  subset(ssid == "362")

events_373<-tmp_jounal2%>%
  subset(ssid == "373")

write_csv(events_362, "events_362.csv")
write_csv(events_373, "events_373.csv")
```
table(dta_journal$ssid)
# trals 16 - 71
# 71-16 = 55 +3
#  55 +3 = 58 triggers we are expectng
# rest 100
# fix and response 101 - 103

unique(dta_journal$label)
as.numeric(dta_journal$label)
as.numeric(unique(dta_journal$label))
unique(dta_journal_1$trigger_label)




dta_journal_1<-


dta_journal%>%
  # subset(ssid == "359")%>%
  mutate(trigger_label = as.numeric(label))%>%
  subset(!is.na(label))%>%
  subset(trigger_label!= 1)%>%
   subset(trigger_label!= 2)%>%
  subset(trigger_label!= 8)%>% 
   subset(trigger_label!= 97)%>%
   subset(trigger_label!= 98)%>%
    group_by(ssid)%>%
  mutate(diff_label = trigger_label -lead(trigger_label))%>%

  mutate(remove_dup = if_else(trigger_label == 103 & diff_label !=2, "remove","keep")) %>%
  mutate(remove_dup = if_else(is.na(remove_dup),"keep",remove_dup))%>%

# %>%  
  subset(remove_dup == "keep")
  # if we don't have 103 before 101 = 


subset(label!= "1")%>%
  subset(label!= "8")%>% 
   subset(label!= "97")
  # subset(trigger_label> 15 & trigger_label<104)
  # this line below here seems to clean out 370 and 373
  # subset(trigger_label < 71|trigger_label> 99)

# unique(dta_journal_1$trigger_label)
# length(unique(dta_journal_1$trigger_label))

# colnames(dta_journal_1)

```{r}
# dta_journal_1$ssid<- substr(dta_journal_1$filename, 1,3)

# range(as.numeric(dta_journal_1$index))

table(dta_journal_1$ssid)

# create a new index
dta_journal_1<- dta_journal_1%>%
  mutate(time_sec = str_remove(time," sec"))%>%
  mutate_at(c('index', 'time_sec','ssid'), as.numeric)%>%
  arrange(ssid, index)%>%
  group_by(ssid)%>%
  mutate(new_index = 1:n())%>%
  mutate(nrows = n())

unique(dta_journal_1$nrows)
range(dta_journal_1$new_index)

table(dta_journal_1$ssid)

# tmp_missing<-subset(dta_journal_1, nrows == 18)
# 
# tmp_missing_223<-subset(dta_journal_1, nrows == 223)
# 
# dta_journal$ssid<- substr(dta_journal$filename,1,3)
# 
# tmp_370<- dta_journal%>%subset(ssid == "370")
# tmp_370<- dta_journal%>%subset(ssid == "373")
# tmp_365<- dta_journal_1%>%subset(ssid == "365")
# 
# tmp_370$
# tmp_366<- dta_journal_1%>%subset(ssid == "366")
# 
# tmp_362$label
# sort(tmp_365$label)
# View(tmp_370)
# sort(tmp_366$label)
# sort(tmp_365$label)
# length(tmp_365$label)
# 67 duplicate

```

"100" "101" "16"  "102" "103" "101" "17"  "102" "103" "101" "18"  "102" "103" "101" "19" 
 [16] "102" "103" "101" "20"  "102" "103" "101" "21"  "102" "103" "101" "22"  "102" "103" "101"
 [31] "37"  "102" "103" "101" "25"  "102" "103" "101" "46"  "102" "103" "101" "62"  "102" "103"
 [46] "101" "56"  "102" "103" "101" "40"  "102" "103" "101" "44"  "102" "103" "101" "31"  "102"
 [61] "103" "101" "57"  "102" "103" "101" "32"  "102" "103" "101" "64"  "102" "103" "101" "33" 
 [76] "102" "103" "101" "41"  "102" "103" "101" "49"  "102" "103" "101" "58"  "102" "103" "101"
 [91] "67"  "102" "103" "101" "23"  "102" "103" "101" "54"  "102" "103" "101" "29"  "102" "103"
[106] "101" "63"  "102" "103" "101" "43"  "102" "103" "101" "51"  "102" "103" "67"  "101" "42" 
[121] "102" "103" "101" "71"  "102" "103" "101" "68"  "102" "103" "101" "45"  "102" "103" "101"
[136] "27"  "102" "103" "101" "66"  "102" "103" "101" "59"  "102" "103" "101" "30"  "102" "103"
[151] "101" "35"  "102" "103" "101" "48"  "102" "103" "101" "52"  "102" "103" "101" "65"  "102"
[166] "103" "101" "24"  "102" "103" "101" "53"  "102" "103" "101" "70"  "102" "103" "101" "60" 
[181] "102" "103" "101" "50"  "102" "103" "101" "61"  "102" "103" "101" "55"  "102" "103" "101"
[196] "69"  "102" "103" "101" "38"  "102" "103" "101" "26"  "102" "103" "101" "36"  "102" "103"
[211] "101" "34"  "102" "103" "101" "39"  "102" "103" "101" "28"  "102" "103" "101" "47"  "102"
[226] "103"

merge journal and ledalab


```{r}
colnames(dta_leda_bio)
dta_journal_1
unique(dta_journal_1$ssid)

length(unique(dta_leda_bio$filename))
dta_leda_bio$filename
dta_leda_bio$filename<-
str_remove(dta_leda_bio$filename,"/Users/heliocuve/Library/CloudStorage/GoogleDrive-helioclemente.c@gmail.com/My Drive/Papers 2022/InteroceptionStudy/InteroStudy2020/Data Collection 2019- 2020/2022/iaps/Preprocessed/Ledalab output/")

dta_leda_bio$ssid<- as.numeric(substr(dta_leda_bio$filename, 1,3))

unique(dta_leda_bio$ssid)
range(dta_leda_bio$event_nr)

dta_leda_bio$event_nr



left_join(dta_leda_bio, dta_journal_1)
table((dta_leda_bio$event_nid))
unique(dta_leda_bio$event_nid)


dta_leda_bio_nid1<- subset(dta_leda_bio, event_nid == "1")


colnames(dta_leda_bio_nid1)
# load 362 and 373

tmp_dta_362_IAPS_Physio_v3_era <- read_csv("~/Library/CloudStorage/GoogleDrive-helioclemente.c@gmail.com/My Drive/Papers 2022/InteroceptionStudy/InteroStudy2020/Data Collection 2019- 2020/2022/iaps/Preprocessed/SCR/362_IAPS_Physio_v3_era.csv")
View(tmp_dta_362_IAPS_Physio_v3_era)


library(readr)
tmp_dta_373_IAPS_Physio_v3_era <- read_csv("~/Library/CloudStorage/GoogleDrive-helioclemente.c@gmail.com/My Drive/Papers 2022/InteroceptionStudy/InteroStudy2020/Data Collection 2019- 2020/2022/iaps/Preprocessed/SCR/373_IAPS_Physio_v3_era.csv")
View(tmp_dta_373_IAPS_Physio_v3_era)

tmp_dta_373_IAPS_Physio_v3_era$filename<- 373
tmp_dta_373_IAPS_Physio_v3_era$ssid <-373

tmp_dta_362_IAPS_Physio_v3_era$filename<- 362
tmp_dta_362_IAPS_Physio_v3_era$ssid<- 362

tmp_dta_362_373<- bind_rows(tmp_dta_362_IAPS_Physio_v3_era,tmp_dta_373_IAPS_Physio_v3_era)

tmp_dta_362_373<- tmp_dta_362_373%>%
  janitor::clean_names()

colnames(dta_leda_bio_nid1)
colnames(tmp_dta_362_373)

tmp_dta_362_373
tmp_dta_362_373$ssid<- as.numeric(tmp_dta_362_373$ssid)
tmp_dta_362_373$filename<- as.character(tmp_dta_362_373$filename)

colnames(dta_leda_bio_nid1)
colnames(tmp_dta_362_373)

tmp_dta_362_373<- tmp_dta_362_373[,c(1,14:15,2:13,16:17)]


colnames(tmp_dta_362_373)<- colnames(dta_leda_bio_nid1)

colnames(dta_leda_bio_nid1)
dta_leda_bio_nid1.1<- bind_rows(dta_leda_bio_nid1, tmp_dta_362_373)

dta_leda_bio_nid1$cda_amp_sum_mu_s
tmp_dta_362_373$cda_amp_sum

dta_leda_bio_nid1

table(dta_leda_bio_nid1.1$ssid)

# table(dta_journal$ssid)
table(dta_journal_1$ssid)





```

table(dta_journal_1$ssid)

```{r}
# table((dta_leda_bio$ssid))
# table(dta_leda_bio_nid1$ssid)
table(dta_leda_bio_nid1.1$ssid)
# tmp_jounal1
table(dta_journal_1$ssid)

table(dta_journal$ssid)


# 365 bio hs one extyra
dta_journal_1
tmp_sid_bio<- subset(dta_leda_bio_nid1.1, ssid == 365)
tmp_sid_journal<- subset(dta_journal, ssid == 366)

tmp_sid_bio<- subset(dta_leda_bio, ssid == 366)
table(tmp_sid_bio$ssid)
366
621
length(tmp_sid_journal$label)
tmp_sid_journal$label
sort(tmp_sid_journal$label)


# check matches
table(dta_leda_bio_nid1.1$ssid)
# tmp_jounal1
table(dta_journal_1$ssid)

table(dta_journal$ssid)
```
"100" "101" "16"  "102" "103" "101" "17"  "102" "103" "101" "18"  "102" "103" "101" "19"  "102" "103" "101" "20"  "102" "103" "101" "21"  "102" "103" "101" "38" 
 [28] "102" "103" "101" "70"  "102" "103" "101" "46"  "102" "103" "101" "33"  "102" "103" "101" "31"  "102" "103" "101" "45"  "102" "103" "101" "53"  "102" "103" "101"
 [55] "55"  "102" "103" "101" "42"  "102" "103" "101" "35"  "102" "103" "101" "51"  "102" "103" "101" "58"  "102" "103" "101" "47"  "102" "103" "101" "26"  "102" "103"
 [82] "101" "36"  "102" "103" "101" "27"  "102" "103" "101" "29"  "102" "103" "101" "48"  "102" "103" "101" "40"  "102" "103" "101" "28"  "102" "103" "101" "65"  "102"
[109] "103" "101" "68"  "102" "103" "101" "63"  "102" "103" "101" "34"  "102" "103" "101" "24"  "102" "103" "101" "61"  "102" "103" "101" "41"  "102" "2"   "103" "101"
[136] "67"  "102" "103" "101" "54"  "102" "103" "101" "25"  "102" "103" "101" "60"  "102" "103" "101" "37"  "102" "103" "101" "32"  "102" "98"  "103" "101" "59"  "102"
[163] "103" "101" "71"  "102" "103" "101" "64"  "102" "103" "101" "62"  "102" "103" "101" "66"  "102" "103" "101" "57"  "102" "103" "101" "23"  "102" "103" "101" "69" 
[190] "102" "103" "101" "43"  "102" "103" "101" "22"  "102" "103" "101" "49"  "102" "103" "101" "39"  "102" "103" "101" "30"  "102" "103" "101" "44"  "102" "103" "101"
[217] "56"  "102" "103" "101" "52"  "102" "103" "101" "50"  "102" "103" NA   


dta_journal_1

# journal has one less for 365
tmp_dta_362_373

```{r}

table(dta_journal$label == "8")

table(dta_journal$label == "98")
table(dta_journal$label == "97")

table(dta_journal$label == "2")

dta_journal_1<-
dta_journal%>%

   # subset( ssid == 366)%>%#bio has 226
  # subset( ssid == 365)%>%
  # subset(ssid == "359")%>%
  mutate(trigger_label = as.numeric(label))%>%
  subset(!is.na(label))%>%
  subset(trigger_label!= 1) %>%
  
    mutate(xtra_359= if_else(ssid == "359" &trigger_label == 8, TRUE, FALSE ))%>%
  subset(xtra_359 == FALSE)%>%
    mutate(xtra_360= if_else(ssid == "360" &trigger_label == 2, TRUE, FALSE ))%>%
   subset(xtra_360 == FALSE)%>%
  
   mutate(xtra_362= if_else(ssid == "362" &trigger_label == 2, TRUE,
                         if_else(ssid == "362" &trigger_label == 1, TRUE,   
                            FALSE )))%>%
   subset(xtra_360 == FALSE)%>%
   subset(xtra_362 == FALSE)%>%
   mutate(xtra_368= if_else(ssid == "368" &trigger_label == 2, TRUE,
                            FALSE ))%>%
   subset(xtra_368 == FALSE)%>%
    # subset(as.numeric(trigger_label)!=8)%>% # 359
    # subset(as.numeric(trigger_label)!=2)%>% # 359
  
   # subset(trigger_label!= 2) %>% #366 consider  subset(ssid ==366 & trigger_label!= 2) 
  mutate(xtra_366 = if_else(ssid == "366" &trigger_label == 98, TRUE, FALSE))%>%
  subset(xtra_366== FALSE) %>%
    mutate(xtra_369 = if_else(ssid == "369" &trigger_label == 2, TRUE, FALSE))%>%
  subset(xtra_369== FALSE) %>%
  
   mutate(xtra_373 = if_else(ssid == "373" & time == "2768.910 sec", TRUE, FALSE))%>% # not sur about this one - [otemtial mimatch]
  subset(xtra_373== FALSE) %>%
  
  mutate(xtra_374 = if_else(ssid == "374" & trigger_label == 2, TRUE, FALSE))%>% 
  subset(xtra_374== FALSE) %>%
  
 mutate(xtra_376 = if_else(ssid == "376" & trigger_label == 2, TRUE, FALSE))%>% 
  subset(xtra_376== FALSE) %>%

   subset(trigger_label!= 97) %>%
  # mutate()
   # subset(ssid == "366" & trigger_label!= 98) %>%
    group_by(ssid)%>%
  mutate(diff_label = trigger_label -lead(trigger_label))%>%
  mutate(remove_dup = if_else(trigger_label == 103 & diff_label !=2, "remove","keep")) %>%
  mutate(remove_dup = if_else(is.na(remove_dup),"keep",
                           if_else(ssid == 365,"keep",  
                              remove_dup)))%>%
# %>%
    subset(remove_dup == "keep")%>%
      group_by(ssid)%>%#
   mutate(new_index = 1:n())


  dta_journal_1$new_index
# %>%  
  
#################  
  # tmp_journal<- dta_journal_1%>%
  #  subset( ssid == "370")
    # tmp_journal%>%
    # mutate(time_sec = as.numeric(str_remove(time," sec")))%>%
    # mutate(lagdif = time_sec-lag(time_sec))
  # i suspect that for 365 there are two cosnecutive numbers below 100

  
   #  tmp_journal<- dta_journal_1%>%
   # subset( ssid == "373") #one potential mismatch
   #  
   #   tmp_journal%>%
   #  mutate(time_sec = as.numeric(str_remove(time," sec")))%>%
   #  mutate(lagdif = time_sec-lag(time_sec)) %>%subset(lagdif<2)
     
# 374
#    tmp_journal<- dta_journal_1%>%
#    subset( ssid == "374") 
# # it just ahs a 2
#      tmp_journal%>%
#     mutate(time_sec = as.numeric(str_remove(time," sec")))%>%
#     mutate(lagdif = time_sec-lag(time_sec)) 
#      subset(lagdif<2)
     
     
     
     # 376
  
     tmp_journal<- dta_journal_1%>%
   subset( ssid == "376") 
# it just ahs a 2
     tmp_journal%>%
    mutate(time_sec = as.numeric(str_remove(time," sec")))%>%
    mutate(lagdif = time_sec-lag(time_sec)) 
     subset(lagdif<2)
     
     # 374
     
          tmp_journal<- dta_journal%>%
   subset( ssid == "375") 
  

  table(tmp_journal$label)
  
  length(tmp_journal$label)
  sort(as.numeric(tmp_journal$label))

  
  # check matches
  
  table(dta_leda_bio_nid1.1$ssid)
# tmp_jounal1
table(dta_journal_1$ssid)

# table(dta_journal$ssid)

# potential mismatches
length(unique( dta_all_merged_sel3.1_trial$ssid))
# 373,362,370

dta_journal_1
```
"100" "101" "16"  "102" "103" "101" "17"  "102" "103" "101" "18"  "102" "103" "101" "19"  "102" "103" "101" "20"  "102" "103" "101" "21"  "102" "103" "101" "46" 
 [28] "102" "103" "101" "26"  "102" "103" "101" "60"  "102" "103" "101" "67"  "102" "103" "101" "58"  "102" "103" "101" "61"  "102" "103" "101" "54"  "102" "103" "101"
 [55] "64"  "102" "103" "101" "57"  "102" "103" "101" "27"  "102" "103" "101" "68"  "102" "103" "101" "36"  "102" "103" "101" "40"  "102" "103" "101" "52"  "102" "103"
 [82] "101" "42"  "102" "103" "101" "38"  "102" "103" "101" "63"  "102" "103" "101" "35"  "102" "103" "101" "56"  "102" "103" "101" "23"  "102" "103" "101" "70"  "102"
[109] "103" "101" "32"  "102" "103" "101" "66"  "102" "103" "101" "71"  "102" "103" "101" "51"  "102" "103" "101" "53"  "102" "103" "101" "45"  "102" "103" "101" "28" 
[136] "102" "103" "101" "30"  "102" "103" "101" "49"  "102" "103" "101" "43"  "102" "103" "101" "44"  "102" "103" "101" "34"  "102" "103" "101" "48"  "102" "103" "101"
[163] "41"  "102" "103" "101" "65"  "102" "103" "101" "55"  "102" "103" "101" "33"  "102" "103" "101" "59"  "102" "103" "101" "47"  "103" "101" "39"  "102" "103" "101"
[190] "29"  "102" "103" "101" "24"  "102" "103" "101" "62"  "102" "103" "101" "69"  "102" "103" "101" "37"  "102" "103" "101" "22"  "102" "103" "101" "31"  "102" "103"
[217] "101" "25"  "102" "103" "101" "50"  "102" "103" NA   
> 
merge ledala lab and joural

```{r}

dta_leda_bio_nid1.1$event_nr

dta_journal_1$event_nr<-
dta_journal_1$new_index

dta_leda_bio_nid1.1$ssid
dta_journal_1$ssid<- as.numeric(dta_journal_1$ssid)


dta_journal_1$event_nr<- as.double(dta_journal_1$event_nr)
dta_journal_1<- dta_journal_1%>%
  # subset(ssid == 375 & trigger_label == 47)%>%
    # subset(ssid == 375 )%>%
  # mutate(fla_375_misingfix = if_else(dta_scr_bio_w_events$trigger_label == 47, event_nr))
  mutate(event_nr = if_else(ssid == 375& event_nr>183, event_nr+1, event_nr))

dta_journal_1%>%
  subset(ssid == 359)

dta_journal_1%>%
  subset(ssid == 375)

dta_scr_bio_w_events<- left_join(dta_leda_bio_nid1.1, dta_journal_1, by = c("event_nr", "ssid"))
table(dta_scr_bio_w_events$ssid)


# 375 after 47, index needs to have +1 o match
dta_scr_bio_w_events
  
table(is.na(dta_scr_bio_w_events$cda_n_scr))

table(dta_scr_bio_w_events$ssid)

dta_scr_bio_w_events1<-dta_scr_bio_w_events%>%
  mutate(extra_365_2= if_else(ssid == 365 & time == "2169.551 sec", TRUE, FALSE))%>%
mutate(extra_366_2= if_else(ssid == 366 & label == "2", TRUE, FALSE))%>%
mutate(extra_621_2= if_else(ssid == 621 & label == "8", TRUE, FALSE))%>%

mutate(extra_622_2= if_else(ssid == 622 & label == "2", TRUE, FALSE))%>%
# 621
  subset(extra_365_2 == FALSE)%>%
   subset(extra_366_2 == FALSE)%>%
  subset(extra_621_2 == FALSE)%>%
   subset(extra_622_2 == FALSE)

table(dta_scr_bio_w_events1$ssid)
# tmp_sid<- subset(dta_scr_bio_w_events, ssid == 365 )
# sort(as.numeric(tmp_sid$label))
# table(as.numeric(tmp_sid$label))
# sort(as.numeric(unique(dta_scr_bio_w_events$label)))
  
  # 366
  
#   tmp_sid<- subset(dta_scr_bio_w_events, ssid == 366 )
# sort(as.numeric(tmp_sid$label))
# table(as.numeric(tmp_sid$label))
# sort(as.numeric(unique(dta_scr_bio_w_events$label)))

# 621

#       tmp_sid<- subset(dta_scr_bio_w_events, ssid == 622 )
# sort(as.numeric(tmp_sid$label)) #8
# table(as.numeric(tmp_sid$label))
# sort(as.numeric(unique(dta_scr_bio_w_events$label)))
  # 622
      tmp_sid<- subset(dta_scr_bio_w_events, ssid == 622 )
sort(as.numeric(tmp_sid$label)) #8
table(as.numeric(tmp_sid$label))
sort(as.numeric(unique(dta_scr_bio_w_events$label)))

# 370,373 NO PROPERR LABELS
table(dta_scr_bio_w_events1$ssid)
     tmp_sid<- subset(dta_scr_bio_w_events, ssid == 362 )
     tmp_sid
  table(dta_leda_bio_nid1.1$ssid)
  
  # MOST FILES CAN BE MERGED BASED ON TRIGGERS/LABEL EXCEPT 370 AND 373, WHICH WE WILL NEED TO DO SOMETHING ABOUT IT
  # MY CURRRNT THOUGH IS TO SELECT JUST TE STIM FROM BEHAVIOURAL DATA, USE STIM ORDER ADD SPACES FOR FIXATION ETC, AND USE THAT TO MATCH WITH EVENT ID
  # 375_ IS MISSING ONE RESPNSE AFTER 184, 

  # HERE
  
  dta_scr_bio_w_events1  #4,717
  dta_scr_bio_w_events1%>%
    subset(label !="100") #4,585 
  dta_bhv_quest1.1_with_fix_resp_arranged #4,704
  
  range(dta_bhv_quest1.1_with_fix_resp_arranged$labels)
  range(dta_bhv_quest1.1_with_fix_resp_arranged$new_index_stim)
  
  
  dta_bhv_quest1.1_with_fix_resp_arranged<-dta_bhv_quest1.1_with_fix_resp_arranged%>%
    group_by(ssid)%>%
    mutate(new_index = 1:n())
  
  range(dta_bhv_quest1.1_with_fix_resp_arranged$new_index)
  table(dta_scr_bio_w_events1$ssid)
  
  range(dta_scr_bio_w_events1$event_nr-1)
  dta_scr_bio_w_events1_norest<- dta_scr_bio_w_events1%>%
    subset(label!= "100")%>%
    group_by(ssid)%>%
    # mutate(new_index = new_index-1)
    mutate(new_index = 1:n(),
           event_nr =1:n()
           )
  
dta_scr_bio_w_events1_norest$event_nr<- as.double(dta_scr_bio_w_events1_norest$event_nr)
  dta_scr_bio_w_events1_norest1<-dta_scr_bio_w_events1_norest%>%
  
   mutate(event_nr = if_else(ssid == 375 & event_nr>183, event_nr+1, event_nr))
  
  range(dta_scr_bio_w_events1_norest$new_index)
range(dta_scr_bio_w_events1_norest$event_nr)

# merge with behav
dta_bhv_quest1.1_with_fix_resp_arranged$ssid<-as.numeric(dta_bhv_quest1.1_with_fix_resp_arranged$ssid)

dta_bhv_quest1.1_with_fix_resp_arranged_scr<- left_join(dta_bhv_quest1.1_with_fix_resp_arranged,dta_scr_bio_w_events1_norest)

dta_bhv_quest1.1_with_fix_resp_arranged_scr
colnames(dta_bhv_quest1.1_with_fix_resp_arranged_scr)

dta_scr_bio_w_events1
colnames(dta_scr_bio_w_events1)
dta_scr_bio_w_events1

unique(dta_scr_bio_w_events1$ssid)
# elixas setr 359+, and 621+
dta_scr_bio_w_events1
colnames(dta_scr_bio_w_events1)

dta_scr_bio_w_events1

dta_scr_bio_359plus_621plus_eliza <- dta_scr_bio_w_events1[,1:27]

# saveRDS(dta_scr_bio_359plus_621plus_eliza, "dta_scr_bio_359plus_621plus_eliza.rds")

dta_scr_bio_359plus_621plus_eliza

colnames(dta_all_merged_eliza)

dta_all_merged_eliza_demog_quest<- dta_all_merged_eliza[,1:43]

require(tidyverse)
```


```{r}

# create tno for elizas dataset

dta_scr_bio_359plus_621plus_eliza$ssid<- as.character(dta_scr_bio_359plus_621plus_eliza$ssid)

dta_all_merged_eliza_demog_quest$ssid<- as.character(dta_all_merged_eliza_demog_quest$ssid)


unique(dta_all_merged_eliza_demog_quest$tNo)
unique(dta_scr_bio_359plus_621plus_eliza$event_nid)


# trigger <- readRDS("~/Library/CloudStorage/GoogleDrive-helioclemente.c@gmail.com/My Drive/Papers 2022/InteroceptionStudy/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/2022_2023_Analyses/Data/EPS/trigger.rds")
dta_scr_bio_359plus_621plus_eliza$event_nr
trigger

dta_scr_bio_359plus_621plus_eliza<- dta_scr_bio_359plus_621plus_eliza%>%
  subset(event_nr>1)%>% # removes rest
  mutate(order = event_nr-1)

# merge with triggers

dta_scr_bio_359plus_621plus_eliza<- left_join(dta_scr_bio_359plus_621plus_eliza, trigger)

dta_all_merged_eliza_demog_quest

dta_scr_bio_359plus_621plus_eliza<- left_join(dta_scr_bio_359plus_621plus_eliza,dta_all_merged_eliza_demog_quest)%>%
  select(-type, - channel,-filename.y, -index_1, -new_index)


dta_scr_bio_359plus_621plus_eliza<- dta_scr_bio_359plus_621plus_eliza%>%
  select(-c(screen_content, screen_content_no, condition.x, condition_no))


dta_scr_bio_359plus_621plus_eliza
```


length(tmp_sid_journal$new_index)
sort(tmp_sid_journal$new_index)-lag(sort(tmp_sid_journal$new_index))
# 373 bio has one less
# 621 bio has one more
# 622 bio has one more

```{r}
tmp_dta_362_373

db_leda_bio<- subset(db_leda_bio, Event.Nr>1)


db_leda_bio<- subset(db_leda_bio, CDA.nSCR!= "NaN")
range(db_leda_bio$Event.Nr)

# transform NaNs into proper NA
db_leda_bio[db_leda_bio == "NaN"] <- NA

# move counter to 1
range(db_leda_bio$Event.Nr-1)
# range(db_leda_bio$Event.Nr)
# trigger$Event.Nr<- NULL

db_leda_bio$order <- db_leda_bio$Event.Nr-1
# db_leda_bio$trigger<- NULL


# merge trigger
trigger$Event.NID<- NULL
trigger$ssid<- NULL
View(db_leda_bio)

db_leda_bio$order
# db_345_355$order

trigger<- db_345_355 %>%
  group_by(order,trigger, tNo)%>%
  summarise_at(c('ssid'), mean, na.rm = TRUE)
  # select(db_345_355, c(trigger, tNo, order))

View(trigger)

  trigger$ssid<- NULL

  nrow(db_leda_bio)
  
  db_leda_bio_beforetrig<- db_leda_bio
  
  db_leda_bio<- left_join(db_leda_bio, trigger)


tmp.df4_sum_full

leda_bioames <- colnames(db_leda_bio)

leda_bioames
newnames<- c("Event.Nr", paste0("BIO_", paste(leda_bioames[2:16])),"BIO_Event.NID","BIO_filename"  ,"ssid","order","trigger")

newnames

db_leda_bio_backup_beforename<- db_leda_bio

colnames(db_leda_bio_backup)

names(db_leda_bio) <- newnames

colnames(db_leda_bio)

# db_leda_bio$ssid <- db_leda_bio$BIO_ssid

# db_leda_bio$BIO_ssid<-NULL


db_leda_bio

db_leda_bio$ssid<- as.character(db_leda_bio$ssid)

# db_leda_bio$order<- db_leda_bio$BIO_order

unique(tmp.df4_sum_full$Event.Nr)

db_leda_bio$BIO_Event.NID <- NULL
db_leda_bio$BIO_filename <- NULL

nrow(tmp.df4_sum_full)
nrow(db_leda_bio)

tmp.df4_sum_full_bio_backup<- tmp.df4_sum_full_bio
tmp.df4_sum_full$ssid<- as.character(tmp.df4_sum_full$ssid)

tmp.df4_sum_full_bio<- left_join(tmp.df4_sum_full,  db_leda_bio, by = c("ssid", "order"))

colnames(tmp.df4_sum_full_bio)


db_leda_bio
write_csv(db_leda_bio, "db_leda_bio_346_347_ledagsr.csv")

write_csv(db_leda_bio, "db_leda_bio_346_355_ledagsr.csv")
```


```