---
title: "MFA - autism vs alexithymia coherence - wide "
output: html_document
date: "2025-12-04"
---


just for MFA
```{r}
# complete the daatset gvia imputation
colnames(dta_vars_4mfa_2_wide)
dta_vars_4mfa_2_wide_sel$tas<-
dta_vars_4mfa_2_wide$tas



dta_vars_4mfa_2_wide_sel<- dta_vars_4mfa_2_wide[,c(1,4:8,9:358)]

dta_vars_4mfa_2_wide_sel$tas_approx<-
dta_vars_4mfa_2_wide$

colnames(dta_vars_4mfa_2_wide_sel)
colnames(dta_vars_4mfa_2_wide_sel[,c(7:256)])
install.packages("missMDA")

dta_vars_4mfa_2_wide_sel_complet <- missMDA::imputeMFA(dta_vars_4mfa_2_wide_sel[,c(7:256)],
                                               ncp=2,
                                               group=c(50,50,50,50,50),
                                        type=c( "s","s","s","s","s"))


# dta_vars_4mfa_2_wide_sel_complet<- bind_cols(dta_vars_4mfa_2_wide_sel[,1:6], 
# dta_vars_4mfa_2_wide_sel_complet$completeObs)
# 
# dta_vars_4mfa_2_wide_sel_complet
# colnames(dta_vars_4mfa_2_wide_sel_complet)
```

mfa
```{r}

dta_vars_4mfa_2_wide_sel_complet

dta_vars_4mfa_2_wide_sel_complet
require(FactoMineR)

mod_res$mfa_z_sid<- FactoMineR::MFA(dta_vars_4mfa_2_wide_sel[,c(7:256)],
             tab.comp=dta_vars_4mfa_2_wide_sel_complet,
              group=c(50,50,50,50,50),
             # type=c( "c","c","c","c","c"),
              type=c("s","s","s","s","s"),
             name.group=c( "scr","hr","pupil","valence","arousal"),
             ncp = 2,
             # num.group.sup=c(1,2),
             graph=TRUE)

mod_res$mfa_z_sid

plot.MFA(resMFA_justvars)


# correlation circle
plot.MFA(mod_res$mfa_z_sid, choix="var",
         select='cos2 0.45',
         habillage='group',
         title="Correlation circle",
         cex=1.5,
         cex.main=0.8,
         cex.axis=0.8)




mod_res$mfa_z_sid$global.pca$eig

```


```{r}
mod_res$mfa_z_sid

fviz_screeplot(mod_res$mfa_z_sid, ncp=5)

fviz_contrib(mod_res$mfa_z_sid, "quanti.var", axes = 1, top = 10)
fviz_contrib(mod_res$mfa_z_sid, "quanti.var", axes = 2,top = 10)
fviz_contrib(mod_res$mfa_z_sid, "quanti.var", axes = 3,top = 10)


dta_vars_4mfa_2_wide_sel$mfa_z_sid_coord_1<- mod_res$mfa_z_sid$ind$coord[,1]
dta_vars_4mfa_2_wide_sel$mfa_z_sid_coord_2<- mod_res$mfa_z_sid$ind$coord[,2]
dta_vars_4mfa_2_wide_sel$mfa_z_sid_coord_3<- mod_res$mfa_z_sid$ind$coord[,3]

dta_vars_4mfa_2_wide_sel$mfa_z_sid_cos2_1<- mod_res$mfa_z_sid$ind$cos2[,1]
dta_vars_4mfa_2_wide_sel$mfa_z_sid_cos2_2<- mod_res$mfa_z_sid$ind$cos2[,2]
dta_vars_4mfa_2_wide_sel$mfa_z_sid_cos2_3<- mod_res$mfa_z_sid$ind$cos2[,3]

dta_vars_4mfa_2_wide_sel$mfa_z_sid_contrib_1<- mod_res$mfa_z_sid$ind$contrib[,1]
dta_vars_4mfa_2_wide_sel$mfa_z_sid_contrib_2<- mod_res$mfa_z_sid$ind$contrib[,2]
dta_vars_4mfa_2_wide_sel$mfa_z_sid_contrib_3<- mod_res$mfa_z_sid$ind$contrib[,3]
```


```{r}

dta_vars_4mfa_2_wide_sel$asd_sid_2<- if_else(dta_vars_4mfa_2_wide_sel$asd_sid != "ASD", "CONTROL",  "ASD")
# correlation with dimensiuon 1
dta_vars_4mfa_2_wide_sel

dta_vars_4mfa_2_wide_sel$aq<- dta_vars_4mfa_2_wide$aq
 
predict(model_tas, newdata = dta_vars_4mfa_2_wide_sel[is.na(dta_vars_4mfa_2_wide_sel$tas), ])
dta_vars_4mfa_2_wide_sel%>%
  subset(asd_sid != "ALEX")%>%
  group_by(asd_sid)%>%
  mutate(tas_approx_z2 = scale(tas))%>%
  # ggplot(aes(tas_approx_z2,mfa_z_sid_coord_1))+
  ggplot(aes(aq2_approx_z,mfa_z_sid_coord_1^2))+
  geom_point(aes(colour = asd_sid))+

  geom_smooth(method = "lm")+
    ggpubr::stat_cor()
  # geom_text(aes(label = ssid))


dta_vars_4mfa_2_wide_sel%>%
  subset(asd_sid != "ALEX")%>%
  group_by(asd_sid)%>%
  mutate(tas_approx_z2 = scale(tas))%>%
  # ggplot(aes(tas_approx_z2,mfa_z_sid_coord_1))+
  ggplot(aes(tas_approx_z,mfa_z_sid_coord_1^2))+
  geom_point(aes(colour = asd_sid))+

  geom_smooth(method = "lm")+
    ggpubr::stat_cor()
  # geom_text(aes(label = ssid))



dta_vars_4mfa_2_wide_sel%>%
  # subset(asd_sid != "ALEX")%>%
  # subset(ssid != 623)%>%
  group_by(asd_sid)%>%
  mutate(tas_approx_z2 = scale(tas))%>%
  # ggplot(aes(tas_approx_z2,mfa_z_sid_coord_1))+
  ggplot(aes(aq2_approx_z,log1p(mfa_z_sid_contrib_1+.1)))+
  geom_point(aes(colour = asd_sid_2))+

  geom_smooth(method = "lm")+
    ggpubr::stat_cor()
  # geom_text(aes(label = ssid))


dta_vars_4mfa_2_wide_sel%>%
  # subset(asd_sid != "ALEX")%>%
   subset(ssid != 623)%>%
  group_by(asd_sid)%>%
  mutate(tas_approx_z2 = scale(tas))%>%
  # ggplot(aes(tas_approx_z2,mfa_z_sid_coord_1))+
  ggplot(aes(tas_approx_z,log1p(mfa_z_sid_contrib_1+.1)))+
  geom_point(aes(colour = asd_sid_2))+

  geom_smooth(method = "lm")+
    ggpubr::stat_cor()



# dim 2
dta_vars_4mfa_2_wide_sel%>%
  # subset(asd_sid != "ALEX")%>%
  # subset(ssid != 623)%>%
  group_by(asd_sid)%>%
  mutate(tas_approx_z2 = scale(tas))%>%
  # ggplot(aes(tas_approx_z2,mfa_z_sid_coord_1))+
  ggplot(aes(aq2_approx_z,(mfa_z_sid_contrib_2+.1)))+
  geom_point(aes(colour = asd_sid_2))+

  geom_smooth(method = "lm")+
    ggpubr::stat_cor()
  # geom_text(aes(label = ssid))


dta_vars_4mfa_2_wide_sel%>%
  subset(asd_sid != "ALEX")%>%
   subset(ssid != 623)%>%
    subset(ssid != 356)%>%
  group_by(asd_sid)%>%
  mutate(tas_approx_z2 = scale(tas))%>%
  # ggplot(aes(tas_approx_z2,mfa_z_sid_coord_1))+
  ggplot(aes(tas_approx_z,(mfa_z_sid_contrib_2)))+
  geom_point(aes(colour = asd_sid_2))+

  geom_smooth(method = "lm")+
    ggpubr::stat_cor()+
    geom_text(aes(label = ssid))

```

dta_vars_4mfa_2_wide_sel%>%
  ggplot(aes(aq2_approx_z,mfa_z_sid_coord_1 ))+
  geom_point()+
  ggpubr::stat_cor()+
  geom_smooth(method = "lm")+
  facet_grid(~asd_sid_2)



dta_vars_4mfa_2_wide_sel%>%
  ggplot(aes(tas_approx_z,log1p(mfa_z_sid_contrib_1+.1 )))+
  geom_point()+
  ggpubr::stat_cor()+
  geom_smooth(method = "lm")+
  facet_grid(~asd_sid_2)


dta_vars_4mfa_2_wide_sel%>%
  ggplot(aes(aq2_approx_z,log1p(mfa_z_sid_contrib_1+.1 ) ))+
  geom_point()+
  ggpubr::stat_cor()+
  geom_smooth(method = "lm")
  facet_grid(~asd_sid_2)


dta_vars_4mfa_2_wide_sel%>%
  ggplot(aes(tas_approx_z,log1p(mfa_z_sid_cos2_1+.1 )))+
  geom_point()+
  ggpubr::stat_cor()+
  geom_smooth(method = "lm")+
  facet_grid(~asd_sid_2)


dta_vars_4mfa_2_wide_sel%>%
  ggplot(aes(aq2_approx_z,log1p(mfa_z_sid_cos2_1+.1 ) ))+
  geom_point()+
  ggpubr::stat_cor()+
  geom_smooth(method = "lm")+
  facet_grid(~asd_sid_2)



dta_vars_4mfa_2_wide_sel%>%
  ggplot(aes(tas_approx_z,mfa_z_sid_coord_2 ))+
  geom_point()+
  ggpubr::stat_cor()+
  geom_smooth(method = "lm")+
facet_grid(~asd_sid_2)


dta_vars_4mfa_2_wide_sel%>%
  ggplot(aes(aq2_approx_z,mfa_z_sid_coord_2 ))+
  geom_point()+
  ggpubr::stat_cor()+
  geom_smooth(method = "lm")+
  facet_grid(~asd_sid_2)



dta_vars_4mfa_2_wide_sel%>%
  ggplot(aes(tas_approx_z,mfa_z_sid_coord_3 ))+
  geom_point()+
  ggpubr::stat_cor()+
  geom_smooth(method = "lm")+
facet_grid(~asd_sid_2)


dta_vars_4mfa_2_wide_sel%>%
  ggplot(aes(aq2_approx_z,mfa_z_sid_coord_3 ))+
  geom_point()+
  ggpubr::stat_cor()+
  geom_smooth(method = "lm")+
  facet_grid(~asd_sid_2)
  


```{r}
cluster

colnames(dta_vars_4mfa_2_wide_sel)
mod_res$kmeans_res_mfa = kmeans(x = dta_vars_4mfa_2_wide_sel[,357:359], centers = 2)


dta_vars_4mfa_2_wide_sel$kmeans_clust<- mod_res$kmeans_res_mfa $cluster


# install.packages("factoextra")



library(cluster)
cluster::clusplot(dta_vars_4mfa_2_wide_sel[,357:359],
         dta_vars_4mfa_2_wide_sel$kmeans_clust,
         lines = 2,
         shade = TRUE,
         color = TRUE,
         labels = 1,
         plotchar = FALSE,
         span = TRUE
         # label = 
         # main = paste('Clusters of customers'),
         # xlab = 'Annual Income',
         # ylab = 'Spending Score'
         )

table(dta_MFA_tas_aq_splits)

dta_vars_4mfa_2_wide_sel%>%
  ggplot(aes(factor(kmeans_clust), mfa_z_sid_contrib_1))+
  geom_jitter(width = .1, alpha = .2)+
  stat_summary(geom = "pointrange")



dta_vars_4mfa_2_wide_sel%>%
  ggplot(aes(factor(kmeans_clust), tas_approx_z))+
  geom_jitter(width = .1, alpha = .2)+
  stat_summary(geom = "pointrange")+
  ggpubr::stat_compare_means()+
    facet_grid(~asd_sid_2)


dta_vars_4mfa_2_wide_sel%>%
  ggplot(aes(factor(kmeans_clust), aq2_approx_z))+
  geom_jitter(width = .1, alpha = .2)+
  stat_summary(geom = "pointrange")+
  ggpubr::stat_compare_means()+
  facet_grid(~asd_sid_2)

```